---
title: "Introduction to argosTrack"
author: "Christoffer Moesgaard Albertsen"
email: "cmoe@aqua.dtu.dk"
date: "`r Sys.Date()`"
bibliography: bib.bib
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to argosTrack}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r knitrsetting, echo=FALSE, results='hide',message=FALSE,warning=FALSE}

knitr::opts_chunk$set(echo=TRUE,error=TRUE,message = TRUE,warning=TRUE,
                      dev='png',fig.ext='png',dpi=72,
                      fig.width=8,fig.height=6)
#setEPS()

```


# Introduction

The `argosTrack` package is intended to model animal movement data collected by the [Argos system](http://www.argos-system.org) with state-space models. It  was originally constructed for the analyzes in @albertsen2015a, which was based on the Continuous Time Correlated Random Walk [@johnson2008a] movement model. Since then, the package has been extended to include several movement models, and is now based on reference classes. The new reference class based implementation gives a moduled based interface that is (hopefully) easier to use, maintain and extend. The package has three types of modules: Observation, Measurement, Movement and Animal. The Observation class is used to contain the data to be modelled. The Measurement class is used to specify the measurement part of the state-space model, which can be done (almost) independently of the actual observations. The Movement classes implements the process part of the state-space model, and finally the Animal class collects the parts to a full state-space model, which can be fitted.

# Included data

The package includes two data sets from @albertsen2015a; a track from a subadult ringed seal and a track from an adult ringed seal. The adult data is accessed by

```{r}

library(argosTrack)
d0 <- adult_ringed_seal
head(d0)

```

Likewise, the subadult data is accessed by

```{r}
d <- subadult_ringed_seal
head(d)
```

We will use the subadult data to illustrate the functionality of the package. For convenience, we remove the 'Z' location class, which is usually considered invalid.

```{r}

d <- subset(d,lc != "Z")

```


# Observation class

The first step in analysing the data using `argosTrack` is collecting the observation data in the Observation class. The input required is the longitudes, latitudes, time stamps and Argos location classes of the track data.

```{r}

obs <- Observation(lon = d$lon,
                   lat = d$lat,
                   dates = as.POSIXct(d$date),
                   locationclass = d$lc
                   )
obs

```

A plot of the track, latitudes over time, and longitudes over time can be produced by the `plot` function

```{r, fig.cap = "Default plot of movement track from subadult ringed seal."}

plot(obs)

```

Each of the plot components can be produced by the functions `plotMap`, `plotLat`, and `plotLon` respectively. The plot functions can be customized by a list of base graphichs arguments as illustrated with the adult ringed seal data.

```{r, fig.cap = "Map of movement track from adult ringed seal."}

dateNum <- as.numeric(as.POSIXct(d0$date)) - as.numeric(as.POSIXct(d0$date[1]))
plotMap(Observation(lon = d0$lon,
                   lat = d0$lat,
                   dates = as.POSIXct(d0$date),
                   locationclass = d0$lc
                   ),args = list(col=as.numeric(d0$lc),
                                 cex = 3 * dateNum/tail(dateNum,1)
                                 )
        )



```



# Measurement class

We now specify the measurement equation of the state-space model using the `Measurement` class. The main argument is `model`, which specifies whether the data should be considered normally distributed (`"n"`) or t-distributed (`"t"`). In this example, we model the measurements by a normal distribution. Another important argument is `nauticalObs`, which specifies whether the observations should be transformed to nautical miles instead of latitudes and longitudes. The default (`FALSE`) is to model the latitudes and longitudes directly.

```{r}

meas <- Measurement(model="n")
meas

```

# Movement class


```{r, echo = FALSE}

allMoveNames <- names(getClass("Movement")@subclasses)

```

The movement model is specified by `Movement` classes. The `Movement` class does not itself implement a movement model, and can not be used directly. Instead, each specific movement model in the package has its own class, which inherits the `Movement` class. Currently, the following classes implements movement models: `r paste(allMoveNames[allMoveNames %in% ls("package:argosTrack")],collapse = ", ")`. Information on each model can be seen in the documentation.

In this example, we use the `RW` class, which implements a random walk model. The class requires the time stamps at which the true position of the animal should be estimated; in our case, this is every (unique) time stamp of the data. By default the time steps are calculated in hours. This can be changed by the `timeunit` argument.

```{r}

mov <- RW(unique(as.POSIXct(d$date)))
mov

```

Like the observations, the `Movement` classes can be plotted.

```{r, fig.cap = "Default plot of a non-fitted movement class."}

plot(mov)

```

Since we have not yet fitted the movement model to data, the plot currently shows the initial values.

# Animal class

To collect the parts, the `Animal` class is used. The class requires an `Observation`, `Movement`, and `Measurement` model. Further, it allows us to give an identifier to the animal.

```{r}

anim <- Animal(obs,mov,meas, as.character(d$id[1]))
anim

```

Using the `plot` function shows a combination of the data from the `Observation` class and the `Movement` class.

```{r, fig.cap = "Default plot of a non-fitted animal class."}

plot(anim)

```



# Maximum likelihood estimation

Maximum likelihood estimation of the model using the Laplace approximation can be done with the `fitTrack` function; a wrapper for a combination of the `TMB` package and `nlminb`. The `silent` argument can be used to reduce the output written to the terminal during optimization. Depending on the movement model, further arguments to combine or fix parameters can be given. More information can be seen in the documentation for each movement model. Note that to speed up the estimation, good starting values have been selected ``behind the scenes'' for this example.


```{r, echo=FALSE}

## Select good starting values
anim$movement$varianceParameters <- c(-3.923820, -3.239427)
anim$measurement$logCorrection <- structure(c(0.6507, 0.8231, -7.14419853802171, -7.49457784080205, 
                                              0.765470866167296, 1.72277724312546, 2.81436897772428, 2.9638286343427, 
                                              2.90849360912734, 3.30810515580851, 4.05506293868793, 4.28114747343453, 
                                              8, 8), .Dim = c(2L, 7L))
anim$measurement$logSdObs <- c(-6.648458, -5.971383)
anim$movement$mu <- structure(c(56.5809855417042, -79.1799473491498, 56.5836211124493, 
-79.1774390738835, 56.6184822609631, -79.1995159505731, 56.6374746265624, 
-79.2198395137131, 56.6389492023984, -79.1502299210697, 56.660868752074, 
-79.1175128261955, 56.6674787026762, -79.1086270455783, 56.7400761167359, 
-79.0257002768612, 56.8376377210478, -78.9448954161691, 56.8567368644532, 
-78.9309431678354, 56.8646874119723, -78.925536826593, 56.8748236569524, 
-78.9185011897533, 56.8750181346451, -78.9183180980792, 56.9118044726103, 
-78.8420755608861, 56.9259319307487, -78.8324706693759, 56.9648427233757, 
-78.7906353330054, 56.971941266102, -78.7844062174804, 57.0204370003417, 
-78.7267390147598, 57.0339648508287, -78.7171216348522, 57.0457609700266, 
-78.7110848752111, 57.0467938786624, -78.7104818547622, 57.0506873488355, 
-78.6865853093875, 57.0494209712403, -78.6839654898198, 57.0445336498007, 
-78.6614370045632, 57.0434374896438, -78.6568721843937, 57.0348108702463, 
-78.5728139862317, 57.0346196543877, -78.5689656067104, 57.0711848125023, 
-78.5636905055252, 57.0769999999744, -78.5619999999884, 57.0884299066879, 
-78.5540610471204, 57.1734903452435, -78.5015141146506, 57.1730333825683, 
-78.502430283669, 57.1689820899789, -78.5059884425337, 57.1587955454663, 
-78.5069878508709, 57.168431599456, -78.5051086497499, 57.1692602751544, 
-78.5041287598286, 57.2842373778344, -78.5250267603042, 57.286267039045, 
-78.5250458594215, 57.2918134957406, -78.5238352494823, 57.3458383612638, 
-78.5061886190815, 57.3474135362983, -78.4961483349708, 57.3497023283655, 
-78.4890157811748, 57.3519999999899, -78.4600000001009, 57.3820392129904, 
-78.3621749892874, 57.3876755622591, -78.3408995023194, 57.3886998147177, 
-78.339525323369, 57.403229149236, -78.3211259781315, 57.4070659722951, 
-78.3131691881042, 57.4086780598938, -78.3108433097311, 57.4053508843145, 
-78.3213730339521, 57.3941538034449, -78.3473250605285, 57.3927008389438, 
-78.344754127183, 57.3928038840062, -78.3450484543963, 57.3926713580048, 
-78.3456460787771, 57.3935127054873, -78.3464300859295, 57.3935285813044, 
-78.3464820719781, 57.3830719699059, -78.3657378976515, 57.3821205289219, 
-78.3667021806476, 57.3808561720684, -78.3676890188005, 57.3768453622129, 
-78.3701197200345, 57.3683098329383, -78.3723209470978, 57.3491801070595, 
-78.3773927259588, 57.327607941139, -78.3878883611096, 57.3213358919484, 
-78.4235339885765, 57.3110000001123, -78.4359999999395, 57.3089927407567, 
-78.4408913944281, 57.2910594263293, -78.4573584758698, 57.2897973430645, 
-78.4558923571499, 57.2869999999947, -78.4590000000096, 57.2860000000307, 
-78.4619999999836, 57.2879999999909, -78.461000000072, 57.3141899494933, 
-78.7076850579253, 57.3169656861001, -78.7329238394055, 57.3182163814355, 
-78.742804426873, 57.3203668570658, -78.7563083609224, 57.3229522936267, 
-78.7607800419117, 57.3232021587376, -78.7611556479699, 57.3262326311874, 
-78.764051931146, 57.3393560743014, -78.7772948978934, 57.341230548465, 
-78.7805154818745, 57.3414103765526, -78.7808877497199, 57.3434201019869, 
-78.8004765407846, 57.3433965100819, -78.8065621006252, 57.3280221579672, 
-78.7267100226304, 57.3260000000301, -78.7320000000215, 57.3559999999823, 
-78.8169999999693, 57.3649999999711, -78.8190000000151, 57.3241934578321, 
-78.8730300276478, 57.3196949314727, -78.8801797513335, 57.3182703059187, 
-78.8832307537739, 57.3163397699588, -78.8856588255186, 57.3157711186561, 
-78.8859811460476, 57.3146485492819, -78.8884881530154, 57.3136165146971, 
-78.8917067556404, 57.3174383934851, -78.8843867449407, 57.3510438716943, 
-78.8155432760705, 57.3518638318344, -78.8136702746316, 57.3673334059229, 
-78.8006093344623, 57.3947784766445, -78.8731695992993, 57.3949439993347, 
-78.8731384598959, 57.4023037156156, -78.8698439418211, 57.4032585885465, 
-78.8645220956801, 57.4036236422532, -78.8623974762606, 57.423499414898, 
-78.800998357479, 57.4269479374284, -78.791193104997, 57.4538324439003, 
-78.7995450951921, 57.4559999999641, -78.7999999999913, 57.4550000000241, 
-78.7990000000384, 57.4690052634017, -78.8810930092813, 57.47122453823, 
-78.9031263578456, 57.4922080677741, -79.0540531144835, 57.4937323137831, 
-79.0609702640883, 57.5052599423459, -79.1072702625394, 57.5446214529246, 
-79.2069497837155, 57.5504172583531, -79.2223972993973, 57.550317019851, 
-79.222471750315, 57.5452310297047, -79.2343489097652, 57.550651680227, 
-79.2533785774077, 57.5545912883995, -79.2680482034846, 57.561540681493, 
-79.2901171552344, 57.5787306623878, -79.3747185134113, 57.5830067463168, 
-79.3892623338582, 57.5915088126126, -79.4168832698526, 57.593407841837, 
-79.4234228652957, 57.597206889713, -79.4334337368768, 57.6031487340981, 
-79.4493282023054, 57.6064818618983, -79.4668842027866, 57.6197296766266, 
-79.5452999593814, 57.6243951145527, -79.5747734403298, 57.6305195521103, 
-79.6001562402668, 57.6308788939635, -79.6014830562201, 57.6306498585345, 
-79.6190014658043, 57.5914143027821, -79.7067082351467, 57.5620000000247, 
-79.8200000000234, 57.5623358952081, -79.824598344148, 57.6069894545622, 
-79.9111766010823, 57.6302004487251, -79.9532471671907, 57.6646303619006, 
-80.0245233988754, 57.6699276579472, -80.0375226294555, 57.6752138617634, 
-80.0554768737663, 57.6794177540816, -80.0669987726055, 57.6831815248212, 
-80.0782523534955, 57.6868125580626, -80.0906464895059, 57.6962019791717, 
-80.121695899185, 57.6967025059177, -80.1235743548971, 57.7472555060489, 
-80.1766757969703, 57.7499593201907, -80.1795934820886, 57.7347397072425, 
-80.2293495133678, 57.7272917401701, -80.2510830389315, 57.7258569466779, 
-80.2547126899067, 57.7279031901912, -80.2657404561409, 57.7526348714721, 
-80.2760649271061, 57.813338552435, -80.295148990315, 57.8151911021199, 
-80.2975761133561, 57.8190905223131, -80.3028791043359, 57.8251373133527, 
-80.3156773499959, 57.8269777290842, -80.3176592707257, 57.8367877151555, 
-80.3321585578133, 57.8474934372592, -80.3582873157476, 57.8559024206005, 
-80.3745560605758, 57.8592133484134, -80.3827294805258, 57.8882087998132, 
-80.454837112613, 57.8971068317103, -80.473806685945, 57.8995170835864, 
-80.4858283057957, 57.9009737934027, -80.4948234377824, 57.9025910541588, 
-80.5022122682345, 57.9097219689975, -80.5352465796577, 57.9426613781173, 
-80.5975078731974, 57.9516044559234, -80.6205291153716, 57.9655935484262, 
-80.6466693831443, 58.0354092012538, -80.7732203854474, 58.0415663911819, 
-80.782795758673, 58.107262317023, -80.8921587480479, 58.133906604715, 
-80.9334729345677, 58.1575210404722, -80.9776421557797, 58.1740978694256, 
-80.9894010589262, 58.197371355049, -81.0072470127853, 58.1997291021782, 
-81.0068628122461, 58.2301098168604, -81.0144580997991, 58.2484865975717, 
-81.0151039411384, 58.2933514287663, -81.0515756861672, 58.3149167985242, 
-81.0690185430719, 58.3256296433911, -81.07884797046, 58.3628426118145, 
-81.1050547230695, 58.4313040660033, -81.1891664820256, 58.442141489531, 
-81.2074423261713, 58.467789095178, -81.2486770185021, 58.4693765564488, 
-81.2513769309523, 58.4792264310883, -81.2691165531954, 58.4958807529672, 
-81.2974351950451, 58.5028319601582, -81.3090625105807, 58.5672625516699, 
-81.4241740558449, 58.6089053510613, -81.4959155395562, 58.6319671384738, 
-81.5340668796484, 58.652176155318, -81.5750318964952, 58.6645049001082, 
-81.6000140729864, 58.6755998061435, -81.6253076778848, 58.6909125190021, 
-81.6542820908277, 58.7238114595939, -81.7154884534048, 58.7354713248154, 
-81.7361136171042, 58.7426472367178, -81.7490011386808, 58.744073526045, 
-81.7514314772203, 58.7662111107185, -81.7886927188587, 58.7734090185322, 
-81.8002901769403, 58.7764683663709, -81.8051274994704, 58.7971280067491, 
-81.8341280217129, 58.8002709611322, -81.8373911713253, 58.803091562298, 
-81.8408993271121, 58.8082382691686, -81.8470590380193, 58.8167295952398, 
-81.8642882941138, 58.8189073610935, -81.8677012213253, 58.8219281541668, 
-81.8729707479741, 58.8257204311691, -81.8781906919468, 58.8296133981807, 
-81.8857810172161, 58.8377131077736, -81.9015087001242, 58.843557578594, 
-81.9105298423885, 58.8981372808199, -82.0127203194505, 58.9029596177965, 
-82.0221997948494, 58.9440056265659, -82.0762796104679, 59.0361551099428, 
-82.1965219406429, 59.0765363236931, -82.2442671586556, 59.0807673214489, 
-82.2492632268129, 59.1036251053467, -82.2968528986623, 59.108875237743, 
-82.3049776422958, 59.125471929275, -82.3304014304044, 59.2445955494961, 
-82.3922775293192, 59.2885586838168, -82.4041902510318, 59.3148157914008, 
-82.4063962701117, 59.3895922183454, -82.5155917057155, 59.4000881186523, 
-82.5292301769336, 59.4146493385241, -82.5477833270339, 59.4435279743641, 
-82.5796890181263, 59.4455399917752, -82.5822571127337, 59.5007522591477, 
-82.5885352000742, 59.5383843175313, -82.5890370539659, 59.544388994548, 
-82.5898840641231, 59.6616455210054, -82.5801326111425, 59.6642815591653, 
-82.5805699618452, 59.7028029480795, -82.5990839309294, 59.7537094289539, 
-82.6252712894449, 59.8060634914477, -82.6558220528311, 59.8118028821043, 
-82.6607309705368, 59.8231025454547, -82.6705070607799, 59.8330624294335, 
-82.6800831874372, 59.8551213222725, -82.6954801691836, 59.8709068210147, 
-82.7046986739788, 59.9915624482929, -82.7770657920775, 59.9981825637374, 
-82.7815617913045, 60.0103343454022, -82.7919904734284, 60.0122002810361, 
-82.7933914809965, 60.0616231893641, -82.8318810840245, 60.074470916713, 
-82.8404404311386, 60.0794108708069, -82.8508408408211, 60.1121539056144, 
-82.8449410462696, 60.1202854102815, -82.8459296883334, 60.1852895595879, 
-82.8584492174753, 60.2236291541842, -82.8728368955465, 60.2590847414984, 
-82.8849526258874, 60.2804673810303, -82.8847217859823, 60.3089889372092, 
-82.890513839016, 60.3122966230526, -82.8905920171738, 60.3588957935175, 
-82.8896210090158, 60.3710605885721, -82.8883077210598, 60.3740012623962, 
-82.8879217939991, 60.3793914670273, -82.8772399372288, 60.3824453119205, 
-82.8565722061341, 60.3876179754606, -82.856404599388, 60.4508605659155, 
-82.8189288305739, 60.4819118580892, -82.8038894879491, 60.4960748862974, 
-82.7956268944139, 60.5638651298665, -82.757001169924, 60.5915603448117, 
-82.7379908717056, 60.6302192230544, -82.7237450962971, 60.6383242044043, 
-82.7233180044545, 60.7433800629307, -82.6935883661528, 60.806093367727, 
-82.7125748312907, 60.8683139712574, -82.7429268400168, 60.8790260878505, 
-82.7208253904431, 60.9192583773259, -82.6630718265272, 60.9479907004725, 
-82.6187901824036, 60.9502407580482, -82.6152459637823, 60.9420992554711, 
-82.5718986066627, 60.9466016046858, -82.5691163619008, 60.953448047727, 
-82.5654417510368, 60.9824059339682, -82.5527313253754, 61.0552554010501, 
-82.5289066628451, 61.0837366969663, -82.5289104539921, 61.1907543922871, 
-82.5917826632576, 61.2921171868179, -82.6895290083393, 61.3294557277711, 
-82.7242515938373, 61.3632432232598, -82.7548077720579, 61.3935965254168, 
-82.8055004553953, 61.4187079974713, -82.8463945952297, 61.4340715712372, 
-82.8618671794997, 61.4846055559155, -82.9652078895503, 61.5038411702931, 
-82.9989765698705, 61.5481295961585, -83.014940088087, 61.5603732428008, 
-83.0225278181542, 61.6083583652982, -83.0600145742177, 61.6153627496079, 
-83.0665286877482, 61.6362171782185, -83.0862554860142, 61.6397401425123, 
-83.089968005428, 61.659449780544, -83.1121585007884, 61.6861591562706, 
-83.0969558503559, 61.6884453848001, -83.0952338489165, 61.7291179936754, 
-83.0638592895348, 61.7502043530654, -83.0429301689696, 61.7849677724095, 
-83.1018776671631, 61.8053314448581, -83.1282658908732, 61.8104071243671, 
-83.1330207047292, 61.8693325465371, -83.1701211066648, 61.877221356044, 
-83.1732269045863, 61.9003073753104, -83.1783565164284, 61.9037116431976, 
-83.1787856174721, 61.9135271188226, -83.1826296860781, 61.931366300322, 
-83.1861562694741, 61.9348706011107, -83.1873677881895, 61.9694397626606, 
-83.1949396461072, 61.9693852752694, -83.2091133628125, 61.970569511573, 
-83.213666514548, 61.9715029262959, -83.2150531795832, 61.9811190390883, 
-83.2110732389289, 62.0445337964118, -83.1782310658928, 62.0487368727182, 
-83.174755425474, 62.0430000000685, -83.1670000000364, 62.0335814974853, 
-83.1511098524509, 62.0740000000271, -83.2710000000261, 62.1650000000033, 
-83.4929999999989, 62.1889999999575, -83.5469999998587, 62.2093187776127, 
-83.2760811275902, 62.2099481049642, -83.2617921483269, 62.2139999998973, 
-83.2370000000609, 62.2006187425296, -83.2289247024759, 62.115935452319, 
-83.2031586688188, 62.1040000000355, -83.1999999999654, 62.1032364037959, 
-83.1979365445043, 62.1007260377249, -83.1905852292697, 62.0960040012903, 
-83.17681002292, 62.0437065673849, -83.0248101185119, 62.0442141292302, 
-83.0250629458045, 62.0447856015469, -83.0321698961104, 62.021000000026, 
-83.2560000000267, 62.0449704893159, -83.5435589752495, 62.0474588353701, 
-83.5693743841633, 62.0503279380651, -83.5964151065979, 62.0623488442766, 
-83.6526041339363, 62.0884200311545, -83.7758790831365, 62.0928240907441, 
-83.7983868889404, 62.0943305084147, -83.8014394427106, 62.0944799939295, 
-83.801396305196, 62.0956267288325, -83.8011980048363, 62.1002856945433, 
-83.8063615890672, 62.2359178253772, -83.9386810164747, 62.236561979787, 
-83.9388014077329, 62.3288592878877, -83.9563952027872, 62.3383341718876, 
-83.9586562166268, 62.4154818508142, -83.98194186642, 62.4160000000145, 
-83.9810000000415, 62.4542783392479, -84.1131641220352, 62.4590149690949, 
-84.1425512376221, 62.4610000003302, -84.1519999997658, 62.4651506615555, 
-84.1470947423353, 62.4632908192701, -84.1411970629481, 62.4663401203125, 
-84.1396166047725, 62.468980913832, -84.1427157860084, 62.5475378173392, 
-84.2157881255033, 62.5538415420949, -84.2196892689848, 62.557636648007, 
-84.212173763035, 62.5621730566108, -83.9736860273072, 62.5382022865988, 
-83.7771135109629, 62.5314555666905, -83.7627735790756, 62.5836207271148, 
-83.7538607608141, 62.5838290205617, -83.7537874290108, 62.5848320815251, 
-83.7550315935463, 62.5872597496023, -83.7507080484194, 62.6400026968707, 
-83.8406476805356, 62.6467731969169, -83.846051382306, 62.6893435149391, 
-83.8801626050079, 62.6892155085921, -83.8799106167173, 62.6081577160324, 
-83.696179652111, 62.6076124429236, -83.6949777418199, 62.5969999997674, 
-83.7030000002883, 62.5940000003665, -83.7089999996779, 62.6527867432837, 
-83.7204273498676, 62.6535493404506, -83.7219142904848, 62.6230000000208, 
-83.6959999999818, 62.6234767770564, -83.6917874255175, 62.6523233247567, 
-83.7004823960882, 62.7182240282223, -83.7157889826489, 62.7208903876864, 
-83.7164912469114, 62.7278021300246, -83.7191125668021, 62.7306838279637, 
-83.7202721716183, 62.8409018827352, -83.7680683087368, 62.8419747439486, 
-83.7686708311425, 62.8451342975461, -83.7800613128019, 62.8479461655893, 
-83.7976971772578, 62.8599515539398, -84.0957792836577, 62.8600000000208, 
-84.1059999999686, 62.8642377437583, -84.1327642830543, 62.9738987139718, 
-84.3207909180266, 63.0658445798459, -84.4798359917855, 63.0669852359103, 
-84.4817806656589, 63.1563562930068, -84.5976812320072, 63.1599897886492, 
-84.6022939508322, 63.1717304411621, -84.6166924528971, 63.1720000000274, 
-84.6169999999925, 63.2713413971554, -84.6575071139516, 63.2705540377443, 
-84.6586301472943, 63.2399999999817, -84.7479999999414, 63.2380000000212, 
-84.7440000000398, 63.1880567294698, -84.7830630715494, 63.1800000000855, 
-84.5929999999766, 63.1805467390598, -84.5919816125022, 63.2023368999963, 
-84.5527972293854, 63.2131599079572, -84.5535701590975, 63.2226490394358, 
-84.5386962944464, 63.2316823527761, -84.5383641855428, 63.2320000000474, 
-84.5360000000433, 63.3010000000593, -84.5520000000049, 63.3059999998811, 
-84.5529999999885, 63.3020352816503, -84.5528749114284, 63.3030000000241, 
-84.5489999999527, 63.3043076951021, -84.5437642431912, 63.3215507475608, 
-84.4796998549017, 63.3289496585806, -84.4411297023641, 63.3329999999791, 
-84.3839999999999, 63.3307114435339, -84.3780841774578, 63.33, 
-84.3759999999899, 63.3276950651354, -84.3663520693725, 63.3253891291668, 
-84.3562291133592, 63.3233975663678, -84.3455497992261, 63.3212061435841, 
-84.3371736932618, 63.3203681360349, -84.3340755410808, 63.2969188031105, 
-84.2705327972848, 63.2966339706542, -84.2672813315489, 63.2941214926477, 
-84.2594120104703, 63.2934717363189, -84.2534173510955, 63.3808835815575, 
-84.3135374100509, 63.3979527646032, -84.3396230037323, 63.3993154662494, 
-84.3418593601248, 63.4917696652254, -84.4081417940282, 63.5419989497829, 
-84.3390623040043, 63.5469411572535, -84.3107920645198, 63.5509773734364, 
-84.2856807918949, 63.5726079441066, -84.1442718195252, 63.5607969325287, 
-84.1246936673121, 63.5500000000172, -84.1100000000762, 63.54706529726, 
-84.1146166164019, 63.5429879536673, -84.1201744844454, 63.5410839369396, 
-84.1227778798022, 63.5002066690735, -84.2183074782063, 63.4974096140042, 
-84.2406434601593, 63.5080137587637, -84.2509541202374, 63.5115884654974, 
-84.2574382684932, 63.516520300347, -84.2664523929224, 63.5271417032904, 
-84.2855914921017, 63.5447641174978, -84.3541073995689, 63.5449828262022, 
-84.3546152089123, 63.5521885189721, -84.355804106209, 63.5559999999609, 
-84.3470000000237, 63.5651694497821, -84.2472918664125, 63.5679999999777, 
-84.2420000000009, 63.5721740528563, -84.1836608181254, 63.5742603067882, 
-84.1812400743029, 63.5810000000013, -84.180000000009, 63.5843650761981, 
-84.1822319094803, 63.6009999994786, -84.2040000000043, 63.5978384713068, 
-84.2041618559693, 63.5950000003484, -84.208999999899, 63.5969999996729, 
-84.2080000000822, 63.5872806234433, -84.2210003491277, 63.5790000002269, 
-84.2329999999578, 63.5822363824504, -84.2346230179594, 63.5631262962228, 
-84.2956465880629, 63.5571306220698, -84.3251511302173, 63.5570170771767, 
-84.3256096869581, 63.5540488853067, -84.3042118928101, 63.5537942736448, 
-84.3031001648998, 63.5541953421391, -84.3026201447611, 63.5543319922129, 
-84.3026861618953, 63.5542183363115, -84.3029083539009, 63.5536482833668, 
-84.3040901755075, 63.543999999969, -84.3229999999946, 63.5410424234932, 
-84.3234867078045, 63.5403253728637, -84.3240087320937, 63.5407586302309, 
-84.3267530916455, 63.5459701670427, -84.3429182281004, 63.5377273743013, 
-84.3387393527889, 63.4459585522401, -84.2764270746094, 63.4427716338174, 
-84.2745365804899, 63.4172889934037, -84.2615797882218, 63.415468810176, 
-84.2601523796696, 63.4135902338335, -84.2586472674027, 63.4030695911563, 
-84.2573767784531, 63.3303135713124, -84.2535798642533, 63.3249142936409, 
-84.2545960472709, 63.3207137831471, -84.2562242382254, 63.3250985733292, 
-84.2860354648822, 63.3459480627271, -84.3865583171065, 63.3474409850409, 
-84.395267886775, 63.3609726714241, -84.4518981583834, 63.3840412835686, 
-84.3763752744235, 63.3907565923258, -84.3565936344253, 63.3876477574828, 
-84.3461725167485, 63.3612025581512, -84.2899644464066, 63.345367650769, 
-84.2686886154283, 63.3402530334859, -84.263568510177, 63.2909574353752, 
-84.2260992515883, 63.2897708904506, -84.2218831930339, 63.2559002615597, 
-84.2552703038347, 63.2554259220804, -84.2611870531814, 63.2741132978731, 
-84.2677873213984, 63.2676918074649, -84.2385960306577, 63.2625030135921, 
-84.2231741947766, 63.2552798273977, -84.2149985367958, 63.2422935607011, 
-84.197153195256, 63.2333554878672, -84.1850657880312, 63.2362757130978, 
-84.1842677566797, 63.2373975471077, -84.1839678604043, 63.2380002661187, 
-84.1837732694663, 63.2391838975734, -84.1835500443467, 63.2529696528131, 
-84.1880457616651, 63.2548355335959, -84.1873625862137, 63.2603276219316, 
-84.1827938269583, 63.2598679194682, -84.1803493257171, 63.2575370602913, 
-84.1841736405187, 63.2503337905955, -84.1864009033404, 63.2487966662663, 
-84.2147553094083, 63.2715988959725, -84.2239864763308, 63.2743806820357, 
-84.2247311296968, 63.3384142262143, -84.2442704950973, 63.3467732658589, 
-84.2392250883094, 63.369461323892, -84.207292413802, 63.3749288383025, 
-84.2069532953907, 63.3844901523966, -84.1989095522663, 63.3892858976387, 
-84.1964551613541, 63.3956367106117, -84.1865616686845, 63.3810000000316, 
-84.0340000000507, 63.3839939488589, -84.0231696904726, 63.3860012199195, 
-84.0170724742216, 63.3899999999882, -84.004000000047, 63.3913669036355, 
-84.0100839879967, 63.399824150745, -84.0510654061186, 63.4015596197779, 
-84.050380850292, 63.4114057425002, -84.0507568265048, 63.4206511542967, 
-84.0516567566764, 63.4427972293017, -84.0676624180786, 63.5417227672599, 
-84.1548194601634, 63.5508762785069, -84.1628012363418, 63.565999999968, 
-84.2189999998885, 63.5706986114117, -84.2124306535445, 63.5727447210687, 
-84.2095254734808, 63.5958950090197, -84.1766789267198, 63.6067658179187, 
-83.9969114209061, 63.5440904234302, -83.8012415867322, 63.536490212223, 
-83.7940440837723, 63.5306364394278, -83.7913562404095, 63.5203609487115, 
-83.7872107817576, 63.5003594128513, -83.7838992304949, 63.4926580942719, 
-83.7846590436615, 63.4739957281053, -83.7862148549373, 63.4257704849106, 
-83.7936617288886, 63.4214289385512, -83.7950478709253, 63.4194451867757, 
-83.7960384577587, 63.4197924032303, -83.7958925148446, 63.421876963536, 
-83.7947236775674, 63.4249387745134, -83.7922002485764, 63.4683260942083, 
-83.7064850769315, 63.500076617887, -83.7013662486032, 63.5166887377381, 
-83.69923557584, 63.6307471371205, -83.6950792818174, 63.6447198554295, 
-83.695406682829, 63.6759511960472, -83.6936560626243, 63.7279086271365, 
-83.6888388392957, 63.7349999998653, -83.6880000000008, 63.7131827054304, 
-83.6863229586443, 63.6884044815472, -83.6857632701412, 63.6669495356703, 
-83.6876505443475, 63.6013910621892, -83.7043046871649, 63.5972494428246, 
-83.7062034988563, 63.5698485101222, -83.6903774443429, 63.5586925903542, 
-83.6762573788657, 63.5388745506862, -83.6527745932418, 63.5347452780646, 
-83.6504899720745, 63.5278399968537, -83.6482710008289, 63.4453542048866, 
-83.6392110678904, 63.4444183432266, -83.6369410675441, 63.4425409625112, 
-83.6375246094448, 63.4332362198441, -83.6407459970112, 63.4293471604898, 
-83.6424157170009, 63.4278482996004, -83.6438024752092, 63.4479156669067, 
-83.6377069781564, 63.4376913912917, -83.6261323107201, 63.4348626928787, 
-83.6212923916226, 63.4304252686835, -83.6131807350762, 63.4085312557536, 
-83.5778692715554, 63.4066526440396, -83.5732554154031, 63.4064054882567, 
-83.5720212083518, 63.4050948599081, -83.5467838965977, 63.4050372697627, 
-83.5455826431319, 63.4051152776171, -83.5422548524682, 63.4062908820835, 
-83.5410062231856, 63.4121498056839, -83.5352891394656, 63.412999999999, 
-83.533999999976, 63.4138243959947, -83.5289743254295, 63.4152530695654, 
-83.5213216626498, 63.4153095652096, -83.449591177227, 63.4187844451852, 
-83.4528251962572, 63.4211739035652, -83.4566167193355, 63.4221725802371, 
-83.4595355320436, 63.4270805387296, -83.4774110536091, 63.43100000003, 
-83.4940000000138, 63.4351069117968, -83.5033952509999, 63.4405188813601, 
-83.516944252608, 63.4411611861211, -83.5189571027857, 63.4850711105078, 
-83.6581639097649, 63.487000000041, -83.6639999999488, 63.492937529072, 
-83.6656958810772, 63.4999695068624, -83.6675101014128, 63.5143158314999, 
-83.6723592067995, 63.6440028446932, -83.7134539873654, 63.6489708940523, 
-83.7152053014331, 63.6695942901542, -83.7295687516302, 63.7045523106757, 
-83.7358878393871, 63.7055369705908, -83.7335152475086, 63.7039999999569, 
-83.7699999999144, 63.7000885192254, -83.7692891008748, 63.6981252461098, 
-83.7689083853536, 63.6954882180387, -83.7691460406194, 63.7046718586752, 
-83.724690660364, 63.7158521287892, -83.7662862211196, 63.715733606059, 
-83.766214855459, 63.7100000000034, -83.7200000000236, 63.7103346993509, 
-83.7320459042347, 63.7168220544159, -83.7555123562266, 63.6656690340847, 
-83.6828793769101, 63.665449772193, -83.6833498978502, 63.6645557973521, 
-83.6841708395782, 63.6669044695195, -83.68493545378, 63.6739952633467, 
-83.6883548435189, 63.6812468517291, -83.6917626238289, 63.7030510448619, 
-83.7026617577945, 63.7056031627212, -83.7039358891961, 63.722003987925, 
-83.7357823496857, 63.7319999999584, -83.7539999999914, 63.7029794460514, 
-83.7776514707448, 63.6556028433994, -83.7320984967943, 63.6277590070854, 
-83.7072762222288, 63.5702935193373, -83.6523966594086, 63.5512965797152, 
-83.630757455124, 63.5429907607446, -83.6187741489343, 63.5277670805275, 
-83.5932118611046, 63.4996322645777, -83.551248211373, 63.4988028599272, 
-83.5499715385106, 63.4912720274957, -83.5333325442096, 63.4890617049453, 
-83.5295704567295, 63.4861730879405, -83.4844296656261, 63.4858207288087, 
-83.4772633441912, 63.4858325305802, -83.477230626022, 63.4889469298005, 
-83.4694500729059, 63.4787549679544, -83.4510476402371, 63.4833587071932, 
-83.517986855226, 63.4831598972402, -83.5174714149551, 63.4809405561537, 
-83.5154150578426, 63.4807742357958, -83.515174506303, 63.4784784044177, 
-83.5165277046594, 63.4786591497506, -83.5159454514485, 63.4808352799114, 
-83.5127087684195, 63.4905617645714, -83.4984131221353, 63.486296970621, 
-83.5049230851808, 63.4560000001078, -83.4999999999665, 63.458122194299, 
-83.4892850376452, 63.4609274868099, -83.4753353197438, 63.4657718191714, 
-83.457692736849, 63.4818640307907, -83.4049524989754, 63.4893694816682, 
-83.3547624139531, 63.4919870515806, -83.3386727223358, 63.5116558118544, 
-83.3236618425933, 63.5135801809569, -83.3202856724901, 63.5220197548594, 
-83.3028124030454, 63.5226184601082, -83.3032159145374, 63.5215959529379, 
-83.303492785639, 63.5202124114697, -83.3021149852738, 63.5157153221822, 
-83.2965626441931, 63.5180725610099, -83.3008282447442, 63.5342431481602, 
-83.3293875234118, 63.5365813483467, -83.3335864466977, 63.5418567991516, 
-83.3438644629254, 63.5435392831749, -83.3480981754568, 63.5468366334329, 
-83.3566798955285, 63.5707747577514, -83.4326736742009, 63.5708789964097, 
-83.434831117777, 63.5687023892477, -83.4388061034473, 63.567000000069, 
-83.4360000000937, 63.5680000000082, -83.5839999999128, 63.5686217851549, 
-83.5768930051285, 63.5561200834141, -83.4968079659401, 63.5119056369726, 
-83.5391117848158, 63.5117916157319, -83.539272098531, 63.5091217205306, 
-83.537183839531, 63.5019999999987, -83.5129999999483, 63.5000000000434, 
-83.4840000001114, 63.5014057087591, -83.4879156712528, 63.508078474986, 
-83.4813522157272, 63.5054171030246, -83.4706990536738, 63.5097577884403, 
-83.4486646515124, 63.5092981923181, -83.4465726265132, 63.5115507392721, 
-83.397464107554, 63.5107133878304, -83.3885913351641, 63.4990955772802, 
-83.332787200894, 63.5200445119195, -83.1914223721823, 63.5255417807811, 
-83.2018890659789, 63.5294726399747, -83.2080639055888, 63.5327953563004, 
-83.2115806320374, 63.5457425510334, -83.2150459176704, 63.5469980228316, 
-83.2160050344912, 63.5495993783384, -83.2169338852863, 63.5494553236966, 
-83.2164834766777, 63.5492861335959, -83.2160463345094, 63.5481489971145, 
-83.21175062716, 63.5474698536473, -83.2091582279367, 63.5464793063791, 
-83.2062897630989, 63.540999999998, -83.1590000000401, 63.5401753075468, 
-83.1632722815498, 63.5377636291759, -83.1754260760267, 63.5376676637627, 
-83.1757782129096, 63.5350273321358, -83.1821780592864, 63.5339648987833, 
-83.1822768735657, 63.5189999999348, -83.1910000000265, 63.5153929667695, 
-83.1938623193966, 63.4960817175346, -83.2745376537144, 63.5025083283667, 
-83.2507804133836, 63.5055702541556, -83.2594020788145, 63.5082553073606, 
-83.2646341046178, 63.5097155316951, -83.2663147884794, 63.5029410857065, 
-83.2684518926449, 63.4987795022907, -83.2705357851051, 63.4905231669851, 
-83.2764249151207, 63.4900230496035, -83.2768383547048, 63.4921398635105, 
-83.2797494316079, 63.4925596138614, -83.2800602510067, 63.5004355929529, 
-83.2853717146059, 63.5009761089994, -83.2850416189259, 63.5009999999939, 
-83.2849999999832, 63.5020437864188, -83.273411246231, 63.4990008826923, 
-83.1856255664563, 63.498099433697, -83.1659357917414, 63.4982980355917, 
-83.1645086309604, 63.4984261431865, -83.1629903922724, 63.4994475837058, 
-83.142665154373, 63.4995040749132, -83.1416354120972, 63.4994981357347, 
-83.1416359846153, 63.4984782549127, -83.1427611759913, 63.4981400349265, 
-83.1543137628278, 63.4993938861922, -83.1555915946517, 63.5025057305337, 
-83.1627040454505, 63.5106178570376, -83.1753962768272, 63.5121568972311, 
-83.1760065919504, 63.5530439362159, -83.1687649556694, 63.5587543009933, 
-83.0960375299451, 63.5562613770357, -83.0797135604245, 63.5554506413055, 
-83.0722156686508, 63.5554171944141, -83.0712341420193, 63.552821139948, 
-83.0225750836122, 63.552284846388, -83.0166865123218, 63.5513446492247, 
-83.0034651467957, 63.552637526991, -83.0052769918143, 63.544219371897, 
-83.0501808666704, 63.5456240064354, -83.049031854431, 63.5368065447871, 
-83.0613393206114, 63.5373062710839, -83.0628751111122, 63.5380701301287, 
-83.061673476654, 63.5425659792239, -83.0578881760777, 63.5689999999958, 
-83.0380000000292, 63.5710000000198, -83.0430000000225, 63.6466341969906, 
-83.2250903502753, 63.7081379395978, -83.3473863780529, 63.7192507760776, 
-83.3693623378538, 63.7199716145221, -83.3753551255852, 63.7053186018234, 
-83.3840086190703, 63.7173988028003, -83.3767901361211, 63.6203748414973, 
-83.2963556029153, 63.6178028044522, -83.3315609217647, 63.6123436812712, 
-83.3268309362022, 63.6117027075797, -83.3263770786723, 63.6084019719755, 
-83.3247019982819, 63.60998544183, -83.333037959147, 63.6120474228264, 
-83.343127599033, 63.6587974280132, -83.3761439207239, 63.6629329881101, 
-83.3763196433395, 63.6737767908026, -83.2413660889084, 63.6723576087807, 
-83.2341251936459, 63.6678486486565, -83.2215930329733, 63.6572230289762, 
-83.193423900372, 63.6566798891137, -83.1918027208775, 63.6553124189575, 
-83.1885244552478, 63.641534366711, -83.1674135547155, 63.6099747500689, 
-83.1156908281786, 63.6091677464557, -83.1144485900785, 63.6089739789223, 
-83.1141539281413, 63.5930000000285, -83.0870000000329, 63.591339158783, 
-83.0874025232622, 63.5911721074529, -83.0873899311034, 63.5909431007719, 
-83.0872719179008, 63.5884298496725, -83.0856939612568, 63.567526322107, 
-83.077159623444, 63.5671983900423, -83.0770767395413, 63.5767845329911, 
-83.0576599447564, 63.5829275353896, -83.050605050134, 63.580414973454, 
-83.0512210599456, 63.5802342854063, -83.0505320161302, 63.5784182509134, 
-83.0422309371331, 63.5801573069663, -82.9863676015905, 63.5769999999853, 
-82.9460000000165, 63.5362207676867, -82.8766878962148, 63.5348982103652, 
-82.874785854004, 63.5299999999919, -82.867999999991, 63.5180580431712, 
-82.8488268101151, 63.5162430051901, -82.8458732406378, 63.5093887732707, 
-82.8340451810364, 63.4990262179141, -82.8137258111521, 63.4983452944155, 
-82.8102197658276, 63.495352117373, -82.793081785312, 63.4929293976243, 
-82.7837317738208, 63.4897411881386, -82.7710796225667, 63.4860000008553, 
-82.7719999996535, 63.4893294715248, -82.7691153766447, 63.4880000000989, 
-82.7590000003708, 63.4884531858957, -82.7636037837481, 63.4900180753049, 
-82.7887479375702, 63.4979999998818, -82.8009999999438, 63.4981149187014, 
-82.8015069402617, 63.5034668760963, -82.8265717893885, 63.5056667517563, 
-82.8358611937522, 63.5014918989672, -82.841522236645, 63.5003508722533, 
-82.841390606578, 63.4987363872426, -82.8422524225553, 63.4980726475401, 
-82.8427042257824, 63.4641517500075, -82.7760453208847, 63.4615010020288, 
-82.7727826335916, 63.4600000000256, -82.7709999999902, 63.4515555491256, 
-82.7431178991298, 63.4479884913089, -82.7266926055716, 63.4470000000153, 
-82.7180000000353, 63.4532370007248, -82.7018910345686, 63.4571043694053, 
-82.694634764028, 63.4628285082534, -82.6811091614904, 63.4670434122146, 
-82.6652741999124, 63.4665318800938, -82.6416632199212, 63.4640621437419, 
-82.6324514210831, 63.4639767812202, -82.6271982290417, 63.4631891468487, 
-82.5807206429646, 63.4631078980491, -82.5756208646851, 63.4629301966064, 
-82.5712638351508, 63.4628331439889, -82.5688101259263, 63.46192499006, 
-82.5749563889838, 63.4655910749463, -82.5522865487368, 63.4661652042255, 
-82.5366765519703, 63.4661413725273, -82.5348508377754, 63.4704734415631, 
-82.5236287673969, 63.4963771702532, -82.456962291907, 63.4976202176975, 
-82.4540973663602, 63.4923226120076, -82.4477118407562, 63.5213304270369, 
-82.5305379889314, 63.5324659472831, -82.5859735511191, 63.5356999903281, 
-82.5914799579648, 63.5001294413922, -82.5571319360773, 63.497000000018, 
-82.5559999999865, 63.4969101431954, -82.5546282426623, 63.4942063168456, 
-82.5428800508299, 63.4975689135771, -82.5417526326826, 63.5103228138992, 
-82.5407909176237, 63.5105627078497, -82.5406196778054, 63.5133023608186, 
-82.5369517065918, 63.5177551596718, -82.5306385133747, 63.5212812220141, 
-82.5228906134272, 63.5624886718363, -82.4535631808308, 63.5679285421564, 
-82.444324384536, 63.5749999999622, -82.4350000000343, 63.5592865006415, 
-82.4858631118267, 63.5559759856443, -82.492590565621, 63.5489096735366, 
-82.5063742559354, 63.5485343747665, -82.5071173487737, 63.5440832563983, 
-82.5307460247852, 63.5433167653031, -82.5336003888877, 63.5434072207032, 
-82.5347281629439, 63.5396829558577, -82.5283066864483, 63.537417150429, 
-82.5274858670885, 63.4866178580574, -82.5078524602227, 63.5002677904333, 
-82.5148321228347, 63.5010191803522, -82.5152280871211, 63.5107220416258, 
-82.5252626820627, 63.5113700948353, -82.5259273285933, 63.5141213285654, 
-82.5250470106586, 63.5183525919687, -82.5192251153212, 63.5222327508554, 
-82.5188056807114, 63.5231929803051, -82.5194381144265, 63.5244412753221, 
-82.5301351186494, 63.5249438894803, -82.5327639494829, 63.525564570574, 
-82.5361708563481, 63.5259105866815, -82.5379335366747, 63.513115439214, 
-82.5751624170348, 63.5104004787734, -82.5812960100379, 63.5054752766407, 
-82.5882950325656, 63.4934679783508, -82.6110276229812, 63.4930501812845, 
-82.6117062061433, 63.489571474895, -82.6147336640283, 63.4836832983304, 
-82.6220483119589, 63.4672700774575, -82.6505440115496, 63.4670000000221, 
-82.6510000000238, 63.4679281750846, -82.6589044269321, 63.4684574672943, 
-82.6665930976377, 63.4684560334213, -82.6673753871406, 63.4678684382908, 
-82.691665791259, 63.4851869433758, -82.7266286845442, 63.4859504592953, 
-82.7301470262919, 63.4865395577589, -82.73331625136, 63.4879999999109, 
-82.7399999999145, 63.4864010795636, -82.7375382307555, 63.4722089473249, 
-82.6519215026763, 63.4713316943221, -82.6465368899742, 63.4702901976691, 
-82.6410855429021, 63.4421584582247, -82.523454749853, 63.4451000053249, 
-82.515185532791, 63.44603845406, -82.5138099498087, 63.453512061867, 
-82.4905281520009, 63.4585265701941, -82.4742251735356, 63.4588085455627, 
-82.4677817156462, 63.4591835951072, -82.4305942636541, 63.4590696857265, 
-82.407571664839, 63.4590024421897, -82.4006646935017, 63.4559000019339, 
-82.3657694801006, 63.4558532765484, -82.3631074711639, 63.4537871096296, 
-82.3075744399417, 63.4541253808939, -82.3026565947216, 63.4522253255831, 
-82.2712403988822, 63.4525741430664, -82.2696160438052, 63.4530892015433, 
-82.2666512867592, 63.4540843959999, -82.2638641908398, 63.4692818608112, 
-82.2384924722472, 63.4741949817338, -82.2295600449569, 63.4773630335541, 
-82.2253616222263, 63.4783590574513, -82.2240255505996, 63.4787058773121, 
-82.2236487220338, 63.4837208217903, -82.2202277804189, 63.5048609749381, 
-82.2087103562036, 63.5088598508422, -82.210536943999, 63.5031833360317, 
-82.2306824918739, 63.4924525810515, -82.262734400391, 63.4906434084385, 
-82.2658721348149, 63.4861303099192, -82.2735829441962, 63.483307901231, 
-82.2942286629752, 63.4825903273375, -82.2987284373345, 63.4813182348072, 
-82.3051771056644, 63.47104070673, -82.3496365095342, 63.4703583546172, 
-82.3529600344349, 63.4679999999966, -82.373999999984, 63.4678732693181, 
-82.3741530673235, 63.4675306645663, -82.3744885006543, 63.4380992889991, 
-82.3932563855014, 63.4388447129263, -82.3753368341074, 63.4389999999718, 
-82.3750000000043, 63.4388016843201, -82.3721852241659, 63.4380000000257, 
-82.3769999998722, 63.4087385328238, -82.2709753684241, 63.407558044157, 
-82.2587979758466, 63.4060881679909, -82.2421096976404, 63.4060049429623, 
-82.2320562578415, 63.4074782494412, -82.2258675682949, 63.4055716543631, 
-82.227260259598, 63.4034916923375, -82.2350072936698, 63.4034418163457, 
-82.2348482832852, 63.3630058143568, -82.1771906094392, 63.3625410510124, 
-82.1764443660275, 63.3624001507721, -82.1759266839021, 63.3624807741543, 
-82.1744502174865, 63.3631424152221, -82.1681037774057, 63.3629730356663, 
-82.1587476521817, 63.3629775570611, -82.1562204416612, 63.3629785784856, 
-82.1555267709136, 63.3628933094323, -82.1533689214086, 63.3649999999591, 
-82.1320000000196, 63.3574194110677, -82.1222587086896, 63.3558915442598, 
-82.1200413957626, 63.3554572776546, -82.1193755294724, 63.3424348434609, 
-82.0803880754327, 63.349424761035, -82.0578546378675, 63.3496525342739, 
-82.0569718363924, 63.3509999999749, -82.052000000058, 63.3509960496712, 
-82.0545950192182, 63.3395125749192, -82.0575116575205, 63.3294514497388, 
-82.0644693138886, 63.3221371472482, -82.07270375163, 63.3218917414838, 
-82.0857637621333, 63.322268272349, -82.0988183317655, 63.322454519412, 
-82.1107856800026, 63.3229172357658, -82.1631478962545, 63.321863399777, 
-82.1852281740044, 63.3219167913302, -82.1919474450085, 63.3207845474119, 
-82.2133336163058, 63.320937601393, -82.2152845779821, 63.3217366649671, 
-82.2195665808492, 63.3218747696728, -82.2210353170763, 63.3134061440004, 
-82.2537424234288, 63.3103075597731, -82.2629467639563, 63.3100000000626, 
-82.2639999999958, 63.3117307097859, -82.2656966821289, 63.3118311897106, 
-82.267655108425, 63.3122983440391, -82.2709556314234, 63.312966644605, 
-82.2816481410226, 63.3085411067777, -82.3285128310969, 63.2784945471184, 
-82.478305330955, 63.2769554616597, -82.4885032658051, 63.2748108498341, 
-82.5042201036096, 63.2738074779264, -82.5245445592473, 63.2755723888468, 
-82.5369253634289, 63.2868633583213, -82.6142827055035, 63.2846050657378, 
-82.6557209994575, 63.2838356174189, -82.6608079487957, 63.2823751524678, 
-82.673195532628, 63.2815950205913, -82.6797990322293, 63.2816707523534, 
-82.6799990943628, 63.2727554868493, -82.7177578879365, 63.2720000000005, 
-82.7209999999772, 63.2694598820875, -82.7218852892602, 63.2691623752479, 
-82.7220973049685, 63.2710928411282, -82.7016271767013, 63.2710961713878, 
-82.6944205609057, 63.2503981063362, -82.6345390670635, 63.2661259109294, 
-82.6696163790964, 63.2818679118743, -82.7458741723629, 63.3013120743434, 
-82.8045229996023, 63.302072517055, -82.8055881502585, 63.3142669207542, 
-82.8236128231021, 63.3225174523692, -82.8357887505558, 63.3554058755345, 
-82.8563617625846, 63.363888313756, -82.8641681496779, 63.3653001736746, 
-82.865738009536, 63.3942200422163, -82.9031177271252, 63.3924673475052, 
-82.924713147052, 63.3880685880631, -82.9316486529923, 63.3854962807741, 
-82.9347640072109, 63.3555827904558, -82.9642184585964, 63.3469909518036, 
-82.9718839214495, 63.3437075082195, -82.9712067600546, 63.3348146299435, 
-82.9875204670094, 63.3346153962171, -82.9871171217717, 63.324008010549, 
-82.9527202496096, 63.3140345618729, -83.0702985989182, 63.3204590657307, 
-83.1714190411458, 63.320601193372, -83.1724995629563, 63.3225280115954, 
-83.2057119922096, 63.3359793934125, -83.253071112773, 63.3390250410627, 
-83.2678476493086, 63.3475367651944, -83.3362373712962, 63.3477072487107, 
-83.3379529717257, 63.3476374878426, -83.3381420355549, 63.3364998896054, 
-83.3679973014968, 63.3347455016018, -83.3758309844232, 63.3312353865702, 
-83.4005804535386, 63.3308470060337, -83.4027510129753, 63.3327227395228, 
-83.4090581350972, 63.3320000003496, -83.4090000000533, 63.3332581157768, 
-83.504904199335, 63.3339756411934, -83.5032576950059, 63.3350530636727, 
-83.5002812689547, 63.3357302048418, -83.4986132212818, 63.3346733008338, 
-83.5131423278197, 63.3352117305573, -83.5138196245437, 63.3334588470653, 
-83.5189192709273, 63.328000000004, -83.485000000057, 63.328954078216, 
-83.6338923548873, 63.3274038264423, -83.6536055346259, 63.3267681283461, 
-83.677705643238, 63.3278991405215, -83.7460499937099, 63.3218105370214, 
-83.7708274091106, 63.3181857032098, -83.7754419676312, 63.3149223466635, 
-83.7731365348848, 63.304275240375, -83.7618512534721, 63.3003305676417, 
-83.7676327180128, 63.2977588414986, -83.7648548716485, 63.2833726651488, 
-83.7512301189713, 63.2813790264778, -83.7497281984375, 63.2730947662881, 
-83.736704628088, 63.2768177040098, -83.7450444521254, 63.2791432193139, 
-83.751175870627, 63.2938976558264, -83.7916747093113, 63.2989999999813, 
-83.8049999998959, 63.3033271624113, -83.7927868696128, 63.3037485633553, 
-83.7914144227187, 63.3319999998818, -83.7090000000245, 63.325000000048, 
-83.7069999999896, 63.3233151543989, -83.7051841997197, 63.3208191191189, 
-83.703169712425, 63.3111656535305, -83.6975253469683, 63.3279999999266, 
-83.6640000000409, 63.3276250664905, -83.6559962401236, 63.327460451113, 
-83.6524632853084, 63.3277076838922, -83.6513842667219, 63.3420280857922, 
-83.5924203647466, 63.3378182783154, -83.598854373216, 63.3342202669585, 
-83.6140304597644, 63.3196927248612, -83.6911841426249, 63.3266647649828, 
-83.6829162185905, 63.3297238678355, -83.6699461662586, 63.3290795329627, 
-83.6665259652991, 63.3224188776518, -83.6309040269145, 63.3461006527348, 
-83.5829156188868, 63.3513391911122, -83.5704485153419, 63.3493298692989, 
-83.5768640548706, 63.3486081374205, -83.5579966179752, 63.3508503260794, 
-83.5345539487409, 63.3497667857014, -83.5364935725621, 63.3420000000609, 
-83.5589999999588, 63.3473234395157, -83.5526384932255, 63.3460309682878, 
-83.5480249604494, 63.3449999999937, -83.5420000002475, 63.3430000000392, 
-83.5579999998177, 63.3430006065028, -83.5494684141963, 63.3431281065294, 
-83.56558061786, 63.3459775097676, -83.5603210407261, 63.3462014275567, 
-83.5603070402273, 63.3770182496697, -83.5594629684124, 63.3771365609068, 
-83.562153138132, 63.3721112159637, -83.6401811271803, 63.3966644634852, 
-83.5478425462826, 63.3900144236782, -83.5328771578942, 63.387146018642, 
-83.5270694660756, 63.3868747492191, -83.5257068831768, 63.3865357616164, 
-83.5242662441024, 63.3859642604728, -83.5220362530241, 63.3830212355393, 
-83.510655770304, 63.3802596335897, -83.4964974027568, 63.3857520538065, 
-83.4516495468554, 63.3785006849857, -83.4382562555797, 63.3750828191007, 
-83.4279087889579, 63.3748912335013, -83.4273182510779, 63.3755734015559, 
-83.4278806826732, 63.3762249642704, -83.4285199441701, 63.3769977593656, 
-83.4289581186951, 63.3774876314723, -83.4272200843393, 63.3772328408512, 
-83.4253514308649, 63.3830568841251, -83.4660397420176, 63.4031691804973, 
-83.489793101515, 63.4075703767501, -83.4899032829481, 63.4079999999052, 
-83.4899999995842, 63.40700000009, -83.4780000004043, 63.4087666165384, 
-83.4763675113285, 63.4084719156124, -83.4767609455372, 63.4018748868745, 
-83.4822244331496, 63.3710504102111, -83.4999213338545, 63.3703057034964, 
-83.5003288920124, 63.3621624419262, -83.49713658414, 63.3539999999733, 
-83.4950000000676, 63.3515912266576, -83.4997756719238, 63.35183361869, 
-83.4998209874084, 63.3530525898294, -83.5000020685464, 63.3536499150887, 
-83.4997916254114, 63.3532888781741, -83.5010112636017, 63.3439871554808, 
-83.5210989241953, 63.3431194015141, -83.5128618315519, 63.3443827716595, 
-83.5079991066467, 63.3469861465704, -83.5004998929318, 63.3508092390258, 
-83.4669976901222, 63.3586439816078, -83.4006328178635, 63.3589999999818, 
-83.3980000000163, 63.3584258107276, -83.3949440276107, 63.3561484432647, 
-83.384122730555, 63.3584100382438, -83.4006044831506, 63.3629999999714, 
-83.4399999998459, 63.3619999999852, -83.4280000001659, 63.3597783413893, 
-83.4340042649973, 63.3590162618776, -83.4359136481311, 63.3567092445176, 
-83.4433434629748, 63.3401217690594, -83.4863792563389, 63.338498265975, 
-83.4905475023034, 63.3408753697256, -83.494181827202, 63.3504887750358, 
-83.5126431420701, 63.3513663278839, -83.5145597911214, 63.3524331810097, 
-83.515645310779, 63.3558407352453, -83.5184893803479, 63.3589592667946, 
-83.5379904410817, 63.3590019352212, -83.5365016911583, 63.3590258056184, 
-83.5303137725567, 63.3615773133618, -83.4828551056726, 63.3619999999058, 
-83.4849999996789, 63.3660990184099, -83.4110979552332, 63.3664922457633, 
-83.3971211361717, 63.3672970038013, -83.3942947040272, 63.3780811273318, 
-83.4373357871999, 63.3829999999981, -83.4730000000174, 63.3839720538305, 
-83.4930884392302, 63.3830269769804, -83.4909785460392, 63.3758183238275, 
-83.4728588733568, 63.3748763664237, -83.4707042099199, 63.3587252558385, 
-83.4959031567321, 63.3624652953583, -83.4894822354667, 63.363832359654, 
-83.4867746282449, 63.3711480409478, -83.4730962159515, 63.3758625730752, 
-83.4578945478534, 63.378678879766, -83.4484701103832, 63.3830149671757, 
-83.4368378970511, 63.3845535946697, -83.434792135574, 63.3843601839673, 
-83.4316545547452, 63.3843358534549, -83.4316181640395, 63.4009999998417, 
-83.4080000002074, 63.3924168461903, -83.4353140020478, 63.3860000001047, 
-83.4469999999353, 63.3669999998235, -83.5489999997052, 63.3640000000615, 
-83.5410000003239, 63.3570497549648, -83.5488204231919, 63.3583342528845, 
-83.5646483176453, 63.3570000002135, -83.5649999999651, 63.3552867121008, 
-83.5391486425941, 63.3550134207134, -83.5433021995722, 63.3550000000095, 
-83.5360000000734, 63.3808923699129, -83.486234071732, 63.3795825215005, 
-83.512918193768, 63.3899635457433, -83.4782460399242, 63.3902068274378, 
-83.4759789797367, 63.3929566984316, -83.4522072004795, 63.3949730700481, 
-83.4358045193459, 63.3978661491166, -83.4076836555257, 63.3977420371577, 
-83.4072114336731, 63.3975789161961, -83.4067196520493, 63.3991831703608, 
-83.4027911099643, 63.4001195034669, -83.4008774340976, 63.4103111324764, 
-83.3772026590911, 63.4117694185712, -83.3738265776999, 63.4109428270642, 
-83.3717066310812, 63.4081457822922, -83.3626784468416, 63.4034452246332, 
-83.3733414848098, 63.4044808644085, -83.3746414768305, 63.4036381917457, 
-83.3770825848859, 63.3977441142809, -83.3939437439967, 63.3959727905792, 
-83.399496031065, 63.3700000000285, -83.4839999999409, 63.3700754731984, 
-83.4826035795097, 63.3701341490882, -83.4772921990295, 63.3699514236821, 
-83.4753402464043, 63.3666202830113, -83.459185144443, 63.3650567963969, 
-83.452057635046, 63.3659540286948, -83.448170215413, 63.3721527434656, 
-83.3972221035604, 63.3757595573833, -83.3856530212777, 63.3727340680857, 
-83.3795375434502, 63.3719715543118, -83.3790088240233, 63.3641930238478, 
-83.3865797938598, 63.3570574134958, -83.392875173553, 63.3564691226725, 
-83.3976798105136, 63.3502560700372, -83.4072453002538, 63.3415656371348, 
-83.4297733783293, 63.3305816936455, -83.4223938210837, 63.3307393713834, 
-83.4185457303937, 63.3318741442288, -83.3946705308133, 63.3327923808425, 
-83.3769574626385, 63.3338437647986, -83.3572049284933, 63.3334694231293, 
-83.3324576590992, 63.3329190121281, -83.3269162955124, 63.3319325453561, 
-83.3243481919237, 63.3283939240762, -83.3172835031747, 63.3493016398457, 
-83.3803689342584, 63.3515789270986, -83.385402514079, 63.3521832676162, 
-83.386718499836, 63.3560511894474, -83.3995510580441, 63.3586756489204, 
-83.4074127919824, 63.3639999999743, -83.4299999999704, 63.3642969627001, 
-83.4372941877486, 63.3643634245158, -83.4401831195081, 63.3649714778516, 
-83.4434464465941, 63.3661292722097, -83.4444284421835, 63.3838952881353, 
-83.4370708135089, 63.3836311640401, -83.4365940165786, 63.3821268367621, 
-83.4332234628776, 63.381000000054, -83.4319999999797, 63.3894388609263, 
-83.4236473015719, 63.3928908006739, -83.420184487888, 63.3950806455928, 
-83.4177857349779, 63.4021574294804, -83.4084393214428, 63.4039339666257, 
-83.4055088967164, 63.4099028317071, -83.3915948476824, 63.4132397144803, 
-83.3781941929746, 63.4389999999228, -83.2670000000592, 63.4365222552547, 
-83.2684066869861, 63.4373890731872, -83.2684081999639, 63.4397573000494, 
-83.2684385551849, 63.4392612452485, -83.2694621455771, 63.4409017159187, 
-83.2699042702926, 63.4812723393625, -83.2631212493734, 63.4840293400715, 
-83.2618942161893, 63.4873006272054, -83.2660010170205, 63.5053487411411, 
-83.2780393594268, 63.5052674721593, -83.2780285515245, 63.5006815550672, 
-83.2750867651499, 63.4972100767343, -83.2731342946077, 63.4965575479903, 
-83.2725774061581, 63.4970885852719, -83.2510989145158, 63.4973630167759, 
-83.2505835745545, 63.4990000000061, -83.247999999959, 63.501103697977, 
-83.2340882882009, 63.5013841673515, -83.2321372224359, 63.5018743627706, 
-83.229008725484, 63.504582606754, -83.2167601503136, 63.5030000000577, 
-83.2080000001092, 63.5220479253735, -83.1981930984705, 63.52297109247, 
-83.1971205166666, 63.5264165278974, -83.1890414631684, 63.528323179216, 
-83.1836353614193, 63.5325407191973, -83.1756896339898, 63.533006155341, 
-83.1818827879823, 63.5323848068314, -83.1855294716253, 63.5240640714643, 
-83.2494665210409, 63.5308250605942, -83.2319689502578, 63.5347171984253, 
-83.2263543912078, 63.5465183555579, -83.2260200434006, 63.5273517835885, 
-83.2152661752288, 63.5213525856705, -83.2128217252646, 63.5181865276861, 
-83.2101353586162, 63.5170344831484, -83.2176736824305, 63.5141423325785, 
-83.226611593721, 63.5120003712205, -83.2316291476033, 63.5107069654985, 
-83.237899179016, 63.5140132429417, -83.2732823958306, 63.5141349865672, 
-83.2742829604822, 63.5189859480123, -83.281601244406, 63.521292803933, 
-83.2898810431158, 63.5296390771612, -83.3074242465237, 63.5302369196282, 
-83.3111813319476, 63.5325113254843, -83.3179582232425, 63.5317799690698, 
-83.3164515659704, 63.5236684756167, -83.3002953413495, 63.521357645747, 
-83.2957449840193, 63.5319067045541, -83.2706797937877, 63.5340250122476, 
-83.2679272893235, 63.5312380861054, -83.2656968854169, 63.5292194952644, 
-83.2655946047886, 63.5257973888236, -83.2669336046199, 63.5147122394944, 
-83.2723459121375, 63.5162350596125, -83.2690960554934, 63.5200243109539, 
-83.2633960260843, 63.5280515334061, -83.2742356487964, 63.5344832520038, 
-83.2680892199496, 63.54030710334, -83.2607771539268, 63.5605340585896, 
-83.2344389754624, 63.565201857756, -83.2301419909134, 63.5718546977834, 
-83.2261445810543, 63.571075728267, -83.2807591538682, 63.5712916410212, 
-83.2818363617211, 63.5730750016282, -83.2895633352602, 63.5754640088988, 
-83.3008626696749, 63.5767968803637, -83.3084291237179, 63.5769104747923, 
-83.3088186095205, 63.5775550461265, -83.3103330000466, 63.5734713758761, 
-83.3041952143804, 63.51353196582, -83.229698484208, 63.5123824424431, 
-83.2283354621463, 63.509000000096, -83.2259999999474, 63.5113722919419, 
-83.2057325178916, 63.5046128191525, -83.1927908976014, 63.4943560624691, 
-83.1728314107081, 63.4900695628271, -83.1554910190654, 63.4850453979341, 
-83.1476162630363, 63.4786072268754, -83.1457475656592, 63.4972349811808, 
-83.1240457109805, 63.4976851242083, -83.1235446667828, 63.4983658855773, 
-83.1231854752761, 63.5037361872745, -83.1204439423629, 63.4750000000191, 
-83.1720000000015, 63.4750334714643, -83.172637170633, 63.4765901901272, 
-83.170534867978, 63.4948316738335, -83.1443221446891, 63.4656912468973, 
-83.1835761153024, 63.4602449571675, -83.1867722961243, 63.4558915194125, 
-83.1907622818863, 63.4547301085361, -83.1911446705271, 63.4488022241169, 
-83.193963054656, 63.4463987648162, -83.1938074100917, 63.4445075455211, 
-83.1928105476919, 63.4494082235795, -83.2126578682917, 63.4499999999646, 
-83.2169999999424, 63.4323902513513, -83.2059082818437, 63.4299809297533, 
-83.2039771083293, 63.4293255183886, -83.203896582593, 63.4223108069019, 
-83.2031664916435, 63.4379999995174, -83.2139999997316, 63.4190000000857, 
-83.1460000001171, 63.4192185857435, -83.1454541006217, 63.4204860862094, 
-83.1423421616694, 63.4181173242564, -83.1430268355149, 63.4081805713918, 
-83.1478009395234, 63.4079918904865, -83.1491424295279, 63.4079510857129, 
-83.1496852273203, 63.4060418280952, -83.1719297537688, 63.409442693349, 
-83.1959559231327, 63.4097473407393, -83.1979812893317, 63.4103099168822, 
-83.2012070609438, 63.4103087673068, -83.2082921219762, 63.4097845303289, 
-83.2443157744335, 63.4102046752667, -83.2504401068953, 63.4142815696759, 
-83.268936441623, 63.4230678993304, -83.2916653134611, 63.4268934117294, 
-83.3074770039651, 63.4269913565332, -83.3082900159954, 63.4221596180874, 
-83.3335507419846, 63.4162883773817, -83.3510420103683, 63.3935213695245, 
-83.4012601241917, 63.3859016476869, -83.4196637355087, 63.375927304446, 
-83.4449749527874, 63.3726205546661, -83.4372158087805, 63.3757370431343, 
-83.4437131732411, 63.3807328796269, -83.4184359961407, 63.3810959183984, 
-83.4077746942719, 63.3804919400839, -83.4072445388273, 63.390005570197, 
-83.3803823725661, 63.3909635215383, -83.3759350190713, 63.3916861481593, 
-83.3750820968267, 63.3930096815592, -83.3731121490556, 63.3961430947085, 
-83.3766342174295, 63.3962498712628, -83.3774961834288, 63.4049735885448, 
-83.4667412103993, 63.4071076205204, -83.4884535091415, 63.4121630562776, 
-83.5412594591986, 63.4139479856884, -83.5610628132276, 63.4252216739047, 
-83.6980976754339, 63.4238913353883, -83.6666228801195, 63.423156380488, 
-83.6511681622427, 63.4199157813347, -83.5377177624942, 63.4168839470457, 
-83.5167144738886, 63.4137843077548, -83.5002616341886, 63.4130425233672, 
-83.4956375855404, 63.4133105497838, -83.4964408115253, 63.4183847684202, 
-83.4980624874094, 63.4224645405904, -83.4982482665014, 63.4186642022207, 
-83.4961392676144, 63.4177390760955, -83.4943287806941, 63.4043766774604, 
-83.4700710109125, 63.4031177330772, -83.4676202801356, 63.4031309706412, 
-83.4613585971163, 63.4030429665456, -83.4577047972755, 63.4030254284364, 
-83.4490304742178, 63.4029330859011, -83.4455726488754, 63.4027601268695, 
-83.4418471210789, 63.3979508450796, -83.3923586498819, 63.3930589994206, 
-83.4175346386401, 63.3917171606274, -83.4227537002806, 63.3874011416892, 
-83.4345325043021, 63.382673617118, -83.4440898252827, 63.3751415448833, 
-83.4575731625599, 63.3724940482793, -83.4949290181814, 63.3721604628458, 
-83.4973821590827, 63.3720000000102, -83.6329999999687, 63.3733569093033, 
-83.6333741847664, 63.3740570656838, -83.6335692827006, 63.3839477452443, 
-83.6307508977969, 63.3868234870227, -83.6297422486633, 63.3880568435114, 
-83.625486866233, 63.3899999999145, -83.6239999999879, 63.3857826750766, 
-83.6219438062709, 63.3781449602463, -83.618304980391, 63.3705854004844, 
-83.6145336885822, 63.3636296978308, -83.6081234078863, 63.3597093014818, 
-83.6043965999267, 63.3494549200827, -83.5944114223516, 63.3465354073251, 
-83.5899189697573, 63.3469772440895, -83.5844531878572, 63.3486446776975, 
-83.5681047788814, 63.3509896851016, -83.5473218808998, 63.3568377257313, 
-83.5180192526727, 63.35610695885, -83.5212140300034, 63.3500510445261, 
-83.5166301154701, 63.3497011558333, -83.490405050438, 63.3536094520416, 
-83.484688020616, 63.3551274872766, -83.4820414353782, 63.3581015940852, 
-83.4762914931336, 63.3586845310421, -83.4747458256994, 63.359150959529, 
-83.4733545748582, 63.3605086016005, -83.4699602831022, 63.3604436865137, 
-83.4695233300785, 63.3600945531785, -83.4687835687848, 63.3597221612044, 
-83.4695826955388, 63.3477271591493, -83.492579327999, 63.3452617642012, 
-83.4971198380431, 63.3427721518317, -83.501614703769, 63.3419999999974, 
-83.5030000000105, 63.3375172264282, -83.5141884914022, 63.3353030259269, 
-83.519603651194, 63.3388406523134, -83.529358120778, 63.3388481433885, 
-83.5275927459743, 63.338801584849, -83.5276339811091, 63.3279127660704, 
-83.5388425804266, 63.3254531839775, -83.5407897822762, 63.3304479736464, 
-83.5360634616352, 63.330549867373, -83.5359624574411, 63.344642790496, 
-83.5296854391813, 63.3606925646286, -83.5218147406051, 63.3752094767055, 
-83.5147433025428, 63.3804023467979, -83.5124744825419, 63.3681897229036, 
-83.5625130488447, 63.3583528523375, -83.6166413289289, 63.3569684984437, 
-83.6266444483209, 63.3607803661785, -83.6244995171867, 63.3662960508108, 
-83.6080369524354, 63.3740997107106, -83.5905307046466, 63.3751414522933, 
-83.5883125760649, 63.3795858091173, -83.5804942158169, 63.3767088971425, 
-83.5804153435246, 63.3755299943609, -83.5803072710189, 63.3666738209189, 
-83.5756633625399, 63.3642712536672, -83.5744034610727, 63.3632734460284, 
-83.5739469143082, 63.3492471383034, -83.5651892456087, 63.3473184422216, 
-83.564805692243, 63.3460263870948, -83.5689527379341, 63.3457729974383, 
-83.5703399638486, 63.3398655147331, -83.606148946221, 63.3397182369422, 
-83.6090457412118, 63.3403022830829, -83.6214611275655, 63.3405026132406, 
-83.6231342603957, 63.3406301856274, -83.6253664588566, 63.3409999999847, 
-83.6309999999765, 63.3397276149861, -83.630488303048, 63.3336180500361, 
-83.6260381454263, 63.3332676386196, -83.6255391984514, 63.3319711861178, 
-83.6228137438595, 63.331369156033, -83.6224791440516, 63.3298047395716, 
-83.6223280337188, 63.3157945323842, -83.6314588757501, 63.304914466572, 
-83.6451550971497, 63.2920749365234, -83.6623750211024, 63.2898565234767, 
-83.6657900223333, 63.2801889358055, -83.6382655022724, 63.2781395843972, 
-83.6268551747867, 63.2768438990146, -83.6192281145026, 63.2799513701456, 
-83.6092175709188, 63.2808657374992, -83.6073461022897, 63.2929128968745, 
-83.5891735801178, 63.2932387086981, -83.5876064207918, 63.2935761663339, 
-83.5861843321954, 63.2931729011853, -83.581917460307, 63.2929693549035, 
-83.5814353281861, 63.2917063028493, -83.5843746748714, 63.2901341753336, 
-83.5883411885775, 63.2877689071625, -83.5939649908391, 63.2691675229032, 
-83.6535368023234, 63.2694875483747, -83.6586154133019, 63.2770373280758, 
-83.6500284793374, 63.2654824813092, -83.671680350871, 63.267000000107, 
-83.6759999997902, 63.2647625696634, -83.6809788392864, 63.2641427042429, 
-83.6829848829044, 63.265543831309, -83.6870696566477, 63.2775668701167, 
-83.7271559928094, 63.2740000000777, -83.7449999998575, 63.2844013278149, 
-83.7269274908082, 63.2906482570869, -83.7094953798995, 63.2987110505392, 
-83.6862167459538, 63.2840700847729, -83.6861225686176, 63.2758158291077, 
-83.6840279657337, 63.2723307250329, -83.6788137021784, 63.2698828533352, 
-83.6740360761851, 63.2937104094873, -83.6352142403764, 63.3112396403527, 
-83.6098706632993, 63.3133296090205, -83.5983931379815, 63.320961707232, 
-83.5696897461936, 63.3220000000058, -83.5660000000339, 63.3237128105598, 
-83.5700936107776, 63.3176064270302, -83.5695026703355, 63.3142179663069, 
-83.5706591600903, 63.3148301479021, -83.5761011983205, 63.2980000000202, 
-83.6260000000203, 63.2981274514355, -83.6301416524432, 63.2972451994955, 
-83.65400122292, 63.2967777806851, -83.6772307537905, 63.2969843438165, 
-83.6785852558825, 63.2978651528576, -83.6827974269851, 63.3036767544835, 
-83.6979554172953, 63.3061642383921, -83.7034217004051, 63.3095186917628, 
-83.7255597797868, 63.3056111541038, -83.7307945616331, 63.3168399691807, 
-83.7259823501245, 63.2825747637761, -83.7183892897409, 63.2862292346503, 
-83.6974531007715, 63.2927921888279, -83.6512210057125, 63.2929481355701, 
-83.6496756278678, 63.2934752046646, -83.6482987382632, 63.2937943728054, 
-83.647850130379, 63.2962640712053, -83.6451131127198, 63.2973590484453, 
-83.6438245670938, 63.2999125847191, -83.6368505021008, 63.3007408803428, 
-83.6283808042164, 63.3017491577461, -83.5998239169256, 63.3011177382602, 
-83.5984717283757, 63.3005320118117, -83.5974383487897, 63.2980778310655, 
-83.5913425906004, 63.297375648096, -83.5895924877392, 63.2692717650591, 
-83.523235466306, 63.2600490586015, -83.5180960988997, 63.2525010945559, 
-83.5138846297621, 63.2522149715487, -83.5138335066066, 63.2480000000772, 
-83.5130000000463, 63.2481789661645, -83.5145186492087, 63.2507469091995, 
-83.5370630511921, 63.2540946668182, -83.5583825687423, 63.2549699359509, 
-83.5631691666461, 63.2723768624532, -83.649042367024, 63.2793472746581, 
-83.6573604402773, 63.3085466846216, -83.6696012330266, 63.3548550986398, 
-83.6880486303469, 63.3549923428065, -83.6632332349535, 63.3452378692807, 
-83.6114306093462, 63.3459350525027, -83.6076235327337, 63.3556279124132, 
-83.5597545777183, 63.3612180201134, -83.5340744318619, 63.3749999999368, 
-83.4689999999911, 63.3713873099854, -83.4546813818924, 63.3688005780409, 
-83.4428906299802, 63.3673664037214, -83.4366290488657, 63.3679999999603, 
-83.4349999999482, 63.361030745919, -83.394881663354, 63.3591827354032, 
-83.3853971342906, 63.3587969515628, -83.3862182753908, 63.3575085488115, 
-83.3867097740956, 63.3573153534314, -83.3868071696495, 63.354526000735, 
-83.3888050416021, 63.3538401061318, -83.3890363303875, 63.3519665916962, 
-83.3974558290562, 63.3512661678333, -83.3995636095581, 63.3270000000163, 
-83.4719999999809, 63.31709498382, -83.5365186583771, 63.3016574875397, 
-83.5618350646052, 63.3027216892983, -83.5618406264166, 63.2999652511203, 
-83.5557779838599, 63.3020320452592, -83.5531631401388, 63.3065847641691, 
-83.528966942846, 63.3081263827947, -83.5206942245011, 63.3127896465739, 
-83.469381516091, 63.3075783251756, -83.4631101442607, 63.3071661867681, 
-83.4625976463611, 63.3074502663904, -83.4589641628173, 63.3075469546051, 
-83.4436288088452, 63.3075413169872, -83.4425736727309, 63.3026234790406, 
-83.4191066890965, 63.3017180141052, -83.4166183978369, 63.2990000000719, 
-83.4120000000277, 63.3035653845926, -83.4125754015987, 63.3064128369589, 
-83.4129236281993, 63.3049084913271, -83.4147295771855, 63.3015513220147, 
-83.4217605387871, 63.3011026968459, -83.4238314666355, 63.3045081220568, 
-83.4228846772199, 63.3077424340926, -83.417774121498, 63.2957941651074, 
-83.3442893674168, 63.2913530003971, -83.3218309785276, 63.2824106283362, 
-83.2843806773946, 63.2738241426771, -83.252102256073, 63.2427605558408, 
-83.2888614913196, 63.2239492386036, -83.3121527557103, 63.2209106725413, 
-83.315545555469, 63.2105032303936, -83.3270359469245, 63.1946249990706, 
-83.337858992851, 63.1917226551638, -83.3396658120113, 63.1859986470072, 
-83.3421487797842, 63.1583743772368, -83.3498998284095, 63.153656174311, 
-83.3510667131774, 63.1494931872329, -83.3495501406538, 63.1457716384297, 
-83.3458405961017, 63.1519365383908, -83.3416647959154, 63.152660090344, 
-83.3412001922638, 63.1535520502655, -83.3401770584196, 63.1550836444945, 
-83.338612083941, 63.1566750505284, -83.3349071280709, 63.1547869571218, 
-83.3320775840674, 63.1484870620139, -83.322280616487, 63.1270000000397, 
-83.2890000000718, 63.1284003537927, -83.2984903802404, 63.1322239578835, 
-83.328137953836, 63.1326173807639, -83.3309378838264, 63.1279201072631, 
-83.3374604982805, 63.1212835720439, -83.3496614135808, 63.1108969637402, 
-83.36823854761, 63.1040655690271, -83.3801062997411, 63.0794112137809, 
-83.42270811576, 63.0713035526559, -83.4359998534842, 63.064361518123, 
-83.4413235258639, 63.0615121600058, -83.4405228545094, 63.0511268910534, 
-83.437284410745, 63.0440808301662, -83.4336765380439, 63.0322978271656, 
-83.4428280198925, 62.9605649861978, -83.5081330680865, 62.94319519142, 
-83.5259667976831, 62.9116532703289, -83.5614047247819, 62.9107742996142, 
-83.5624581682124, 62.8980427166489, -83.5873163165539, 62.8820905711367, 
-83.6197858757584, 62.8818340690098, -83.6213002170059, 62.8780876251643, 
-83.6525341755332, 62.8765409863301, -83.6779775876075, 62.876161022596, 
-83.7268847595144, 62.8764922255865, -83.742926493989, 62.8892136739069, 
-83.7586825712024, 62.8941869610134, -83.7637372563621, 62.9037042991108, 
-83.7723725048013, 62.9056476264222, -83.774926596547, 62.9061692821239, 
-83.775792795531, 62.9112179750743, -83.7861736158462, 62.9255158247211, 
-83.804855268627, 62.9262413825594, -83.8072910351404, 62.9431283458572, 
-83.8836195158095, 62.9503668175992, -83.9118446867775, 62.9511876438552, 
-83.9151503657323, 62.9526002142645, -83.9207889453523, 62.9586790715772, 
-83.9416564563565, 62.9545177083933, -83.9539711985901, 62.9542021059881, 
-83.9588546239507, 62.9729277864271, -84.0804758713527, 62.9751285878246, 
-84.1021874755212, 62.9754567301046, -84.1066564125175, 62.9769533837324, 
-84.1203565456591, 62.9785631883949, -84.1281584140466, 62.9795652194884, 
-84.1316051198456, 62.9766955558823, -84.139472680367, 62.9749999999538, 
-84.137999999952, 62.9721638593747, -84.1328619159904, 62.9642906580144, 
-84.1249359243366, 62.9679948060172, -84.1253636406272, 62.975370808027, 
-84.1201005630076, 62.9759273488018, -84.1195256543721, 62.9793211317995, 
-84.1157365647875, 62.979836170766, -84.1155508662228, 62.9822129364778, 
-84.1147978130621, 63.0048874255197, -84.1103006025617, 63.0049852723564, 
-84.1097311964093, 63.0030571908566, -84.1081141575226, 63.0034186775686, 
-84.1090245736742, 63.0035000438092, -84.1091553292179, 63.0038724311616, 
-84.1094260663932, 63.0278606500303, -84.1188847858295, 63.0310853696418, 
-84.1206843958889, 63.0373544600009, -84.1239651496564, 63.0391780760802, 
-84.1251067610919, 63.0419819902216, -84.1279751474242, 63.0879190934631, 
-84.1771956992159, 63.0908240509377, -84.1831501037914, 63.0913744890291, 
-84.1871993351277, 63.0908540213805, -84.1880667073794, 63.0911231035935, 
-84.1876857659841, 63.0963323859954, -84.188691151995, 63.0966872274893, 
-84.1888527113091, 63.0970207091068, -84.1885437497588, 63.0964415842609, 
-84.184242597776, 63.0962080070165, -84.1831133434811, 63.0968011459694, 
-84.1815610885745, 63.099917348666, -84.1710761504023, 63.100861828747, 
-84.167840160438, 63.1028686975545, -84.176964487001, 63.0981307906186, 
-84.1861580714187, 63.1060901572072, -84.1689143160823, 63.1070000000126, 
-84.1670000000047, 63.110622500857, -84.164580501865, 63.1259267841191, 
-84.1506549688798, 63.1285468747454, -84.1485996149625, 63.1270775783647, 
-84.1558822897136, 63.1269406037501, -84.1512791730417, 63.1302352278891, 
-84.1361200805448, 63.128419735857, -84.1487958280522, 63.1192904710512, 
-84.1950229262982, 63.1186336391681, -84.1989960385207, 63.1176444766377, 
-84.2050906915503, 63.1152040616428, -84.2155222917724, 63.1151874245152, 
-84.2232168914533, 63.1180690908146, -84.212358388102, 63.1497675636938, 
-84.0907660046624, 63.1565561461108, -84.0712601462845, 63.1574567010878, 
-84.0680687656254, 63.1586706130001, -84.0622980474761, 63.1616473354537, 
-84.0486496010336, 63.1631377757673, -84.0241352589591, 63.1635421611443, 
-84.0240895944487, 63.1645632582049, -84.0221780655821, 63.2008796152185, 
-83.9515143042141, 63.2109312893142, -83.9333351793937, 63.2168742501806, 
-83.9215621711468, 63.2171100117472, -83.920617363766, 63.2134444702869, 
-83.9194916469536, 63.2130838978287, -83.9184916750996, 63.2097041719381, 
-83.9122477718297, 63.1991429569052, -83.8228988778459, 63.2012569781623, 
-83.8305074366884, 63.2097023930462, -83.8607093398124, 63.2133616419723, 
-83.8738573797271, 63.2183532455623, -83.8936858402418, 63.2193221216145, 
-83.9078393041249, 63.219110938273, -84.0202807385653, 63.2202347791255, 
-84.0369601305455, 63.2206182470492, -84.0489291109952, 63.2239999999022, 
-84.0489999999554, 63.2229392139355, -84.0413805251423, 63.2224147612456, 
-84.0376929443595, 63.2200000000003, -84.0130000000243, 63.2128174458978, 
-83.9799008941261, 63.2120000000612, -83.9770000000176, 63.2121137649768, 
-83.9769717072249, 63.2124093742296, -83.9761464750041, 63.2154602145281, 
-83.9592098954172, 63.2161279195335, -83.9528595064717, 63.2171873640285, 
-83.9525398278233, 63.2181167880473, -83.9520989094023, 63.2184081595822, 
-83.9519603250194, 63.2189242325357, -83.9517259359441, 63.2407048968362, 
-83.9342845309166, 63.240208995129, -83.9345977946392, 63.2532086788855, 
-83.82902396038, 63.2751715300843, -83.8475362448271, 63.2627824687502, 
-83.77995087785, 63.2625903540735, -83.778581926307, 63.2623884975053, 
-83.7774479490023, 63.2610665418595, -83.7696625925151, 63.2638643660827, 
-83.7694601326792, 63.3008357135546, -83.7685372115823, 63.3055742583263, 
-83.7686666898172, 63.305774790808, -83.7699530355947, 63.3071699039225, 
-83.7768677632422, 63.3072772852232, -83.7775317494807, 63.3092075357298, 
-83.7950214622497, 63.3067991530763, -83.7900995302719, 63.3047319010092, 
-83.783231878768, 63.3067558824194, -83.7769224775716, 63.3068024927782, 
-83.7768919369301, 63.30645338455, -83.7779705041743, 63.3057940806196, 
-83.7779793502416, 63.3064445074751, -83.7606463789038, 63.3065969792002, 
-83.7554317628472, 63.3056715110465, -83.7505288721023, 63.3038099321948, 
-83.72890347563, 63.3031918253334, -83.7245238770918, 63.2998956427103, 
-83.7006874548264, 63.3016786931598, -83.6904966232778, 63.2989948672837, 
-83.7252957162734, 63.2991430049039, -83.7266193484996, 63.2999987353029, 
-83.732351638228, 63.3025072392425, -83.7423447554886, 63.3025087532145, 
-83.7423492701063, 63.3110561493741, -83.7566910866762, 63.3133332807784, 
-83.7603708478773, 63.3257804413, -83.7734613358442, 63.3330716162529, 
-83.7833025897499, 63.3438274353776, -83.7911798241396, 63.3456115621703, 
-83.7926012230899, 63.3528361407643, -83.7967243697882, 63.3664153156327, 
-83.7952470596624, 63.3709245843709, -83.7963428041667, 63.3722852729277, 
-83.7964473968736, 63.3661494036174, -83.8244646936633, 63.3577955913602, 
-83.860439353364, 63.3573835519153, -83.8635551538011, 63.3558158560036, 
-83.8700445988835, 63.3521698304382, -83.88288598358, 63.3408806502884, 
-83.9116651930007, 63.3396786003209, -83.9214292128194, 63.3423375934697, 
-83.9280130883423, 63.3496830273073, -83.9254537228878, 63.3518805467755, 
-83.9248483487743, 63.3685598823554, -83.8636424461477, 63.3692471918005, 
-83.8607763293119, 63.3699968297424, -83.8575102237978, 63.3721874014219, 
-83.8463731972466, 63.3702682235503, -83.8442516373332, 63.3700000000143, 
-83.843999999965, 63.3703665857775, -83.8394693674018, 63.3699296793894, 
-83.8290684234987, 63.3726206675481, -83.7631904614245, 63.3729865157713, 
-83.7578119651349, 63.3762109135155, -83.752791126393, 63.3785647879691, 
-83.7469178045049, 63.3970552364696, -83.7038013758846, 63.3896621814521, 
-83.6930711856581, 63.3898646371972, -83.6958317759908, 63.3900328038571, 
-83.6977067233482, 63.3931231285351, -83.6977119401424, 63.3938185336501, 
-83.6978642048616, 63.4063716786211, -83.7040878215924, 63.4076723114598, 
-83.705168043882, 63.4079736778068, -83.7053567075058, 63.4103344514484, 
-83.6945117561173, 63.4108875064353, -83.709180803165, 63.4109503874807, 
-83.7108377418401, 63.4119081012118, -83.7635380095115, 63.411909725571, 
-83.7659232070101, 63.4110245682843, -83.7846547505053, 63.4102274530329, 
-83.8005128078799, 63.41, -83.8149999999835, 63.4096043436874, 
-83.8211966841403, 63.4116409083962, -83.8252621929009, 63.4111808594447, 
-83.8292024221154, 63.4180003269954, -83.827407028617, 63.4210910808735, 
-83.8267084712363, 63.4293521053048, -83.7803699268282, 63.4301554064269, 
-83.7632251068088, 63.4300675223499, -83.762579874763, 63.4282114921935, 
-83.7526663803, 63.429187625944, -83.7482214701848, 63.4407619866103, 
-83.6909395903827, 63.4368230789106, -83.6847201962108, 63.4363657093577, 
-83.6841409186377, 63.4451253766896, -83.6845515473911, 63.4462826361924, 
-83.6844890945625, 63.4770186913056, -83.6808113956782, 63.4857017339367, 
-83.6714675785175, 63.4858762698796, -83.6713024433352, 63.4902716329223, 
-83.6821122205756, 63.490790909434, -83.683566941301, 63.4953361386057, 
-83.6960983700894, 63.4956744291875, -83.7088262098757, 63.4948239450059, 
-83.7315883054799, 63.4936347455649, -83.725891406053, 63.4890000000676, 
-83.7309999999552, 63.4919891796917, -83.7241258319023, 63.4951720266265, 
-83.7266416336673, 63.495181660622, -83.7274222031528, 63.5159821614485, 
-83.7258607492758, 63.517659583606, -83.7259800553979, 63.5120364693526, 
-83.7030452217002, 63.51171486115, -83.702203564253, 63.5105945904224, 
-83.6990599327274, 63.509405650112, -83.694063790181, 63.5078458865037, 
-83.6941776991744, 63.4982340455646, -83.6967898489556, 63.476991307744, 
-83.7091394877888, 63.4749520970425, -83.7098873244996, 63.4640351761074, 
-83.7402757880629, 63.4636768435572, -83.7422971013704, 63.4636715092273, 
-83.7441054710523, 63.4639879335555, -83.7524259383601, 63.4709844963112, 
-83.7334074589675, 63.4744123593035, -83.7196970201571, 63.4809468322174, 
-83.6916032081154, 63.4877891829065, -83.663122966442, 63.4906248982375, 
-83.6525705749641, 63.4946881980708, -83.634018298032, 63.5008849772083, 
-83.6223446427656, 63.4981875724445, -83.6420841499411, 63.5008620036668, 
-83.6533483295393, 63.4978620270084, -83.6601513881761, 63.4868424945021, 
-83.6873032039191, 63.4820000000336, -83.700999999948, 63.4830872550774, 
-83.6974889185146, 63.4835295540137, -83.6959479887229, 63.4915541378036, 
-83.667132108082, 63.5038035430324, -83.6234146714222, 63.5037671602919, 
-83.6286820916849, 63.5012586196374, -83.6391062255625, 63.4960181699636, 
-83.6551414533293, 63.4840385995409, -83.7238961255276, 63.4809227214444, 
-83.7383929806059, 63.4755152482397, -83.7647325416006, 63.4736787273309, 
-83.7735180163594, 63.4733587977051, -83.7752856328203, 63.5069999999806, 
-83.7070000000175, 63.5091564994381, -83.7020254267509, 63.522207735973, 
-83.6700105970419, 63.5264802372877, -83.6596207663388, 63.5265319488905, 
-83.6595243440948, 63.5402920915637, -83.6426983646299, 63.5454323137439, 
-83.6380481735811, 63.5467802587086, -83.6302138111581, 63.5656550628744, 
-83.5497388935398, 63.5659780728478, -83.5479560026748, 63.5667905333805, 
-83.5195054860426, 63.5669687170525, -83.5148762226302, 63.567317663771, 
-83.5114333266113, 63.5683127611632, -83.5122373021678, 63.5698199121833, 
-83.5106998980197, 63.5820356946387, -83.4969440469874, 63.5629026114197, 
-83.4975846897396, 63.5584191700446, -83.4986343444447, 63.5542106960106, 
-83.4996654463526, 63.5509330195748, -83.4988646956748, 63.5480322769694, 
-83.4920854929622, 63.5194651678168, -83.5363936002374, 63.5183960055787, 
-83.5375494274757, 63.5184823951094, -83.5451587611321, 63.5185481617604, 
-83.5481178200111, 63.5196854510141, -83.5793321410321, 63.5197059084654, 
-83.5808854287675, 63.5205453605204, -83.586513512926, 63.5207562816871, 
-83.5868970440567, 63.5294776643016, -83.6108499215878, 63.5300000002634, 
-83.6119999997538, 63.534381331862, -83.6041262668337, 63.5271148896301, 
-83.6365818134361, 63.5306915406899, -83.6450006767332, 63.5261989382238, 
-83.6339836955115, 63.5257305587504, -83.6286755267417, 63.5219964741847, 
-83.5718469747382, 63.5207413694371, -83.5357911330462, 63.5220779782799, 
-83.5273736882021, 63.5270571938614, -83.5223642609239, 63.5286309652134, 
-83.5209556857432, 63.5285906439073, -83.5211813276134, 63.5358389482666, 
-83.4967611747754, 63.5401745140124, -83.4871015440673, 63.5401111072277, 
-83.4870849699327, 63.5401658703726, -83.4852947948578, 63.5396707172304, 
-83.4716846469143, 63.5340000000551, -83.481999999994, 63.5450644732088, 
-83.5721589771108, 63.5478429898477, -83.5865459321082, 63.5480677129439, 
-83.5886231371802, 63.5821028522888, -83.5526830179763, 63.5826433732322, 
-83.5517388163996, 63.6065568694998, -83.4866804669721, 63.6044656907039, 
-83.490195701399, 63.5930771585226, -83.5083600686456, 63.5840000001389, 
-83.5279999998929, 63.5889999998777, -83.5210000000368, 63.5848427512027, 
-83.5011714896654, 63.5698313936803, -83.4303031371037, 63.5692875135002, 
-83.4270581899957, 63.5654823924011, -83.4003999445791, 63.5602892798874, 
-83.3613052310794, 63.5595408505949, -83.3561443801069, 63.5550714894001, 
-83.3287785303406, 63.5542461329837, -83.3240596711302, 63.5464760184663, 
-83.2838014669164, 63.5539741266484, -83.2860164417956, 63.5749666684071, 
-83.2345536407654, 63.5758528530349, -83.2325501916259, 63.5784240244266, 
-83.2279849109964, 63.5792769323125, -83.2290001751025, 63.5796938418844, 
-83.2294364329115, 63.5857187881096, -83.2371475151858, 63.5873100347466, 
-83.2410836397852, 63.5872451122505, -83.2417114097627, 63.5803439748081, 
-83.2764217626344, 63.5801829984629, -83.2780358289145, 63.5904958442217, 
-83.3514583148425, 63.5956041465781, -83.4768701175387, 63.5850000002275, 
-83.4620000001798, 63.5828339478613, -83.473851798989, 63.5803456298103, 
-83.4843864093281, 63.5805892463841, -83.4857703914036, 63.581725306823, 
-83.492723941272, 63.5866374507465, -83.4978022873485, 63.5931908533243, 
-83.4998057199887, 63.5570416906416, -83.4607884198775, 63.5545050657043, 
-83.4553519470229, 63.5484797226067, -83.4416532367741, 63.5482289480351, 
-83.4411364918649, 63.5454255270881, -83.4376376432921, 63.538707757927, 
-83.4305437342068, 63.5349443911639, -83.4280641554993, 63.5337851679556, 
-83.4277025657226, 63.5314548421379, -83.4275575726667, 63.5102950802387, 
-83.4289010290393, 63.5102376134398, -83.4289081583649, 63.5107374257625, 
-83.4319489267752, 63.5116041207643, -83.4368287973338, 63.5123074747416, 
-83.440300480265, 63.512928434732, -83.4412706340563, 63.52010772263, 
-83.4539390404266, 63.5374594810435, -83.4866090125038, 63.5391211925411, 
-83.4898234660691, 63.5397650404362, -83.4907884558305, 63.551265772289, 
-83.5082512687798, 63.5526662414648, -83.5103030586156, 63.5716544868093, 
-83.5372619717806, 63.5770377066763, -83.547935610512, 63.5814912156687, 
-83.5598863937923, 63.587117852598, -83.5846915211823, 63.5879262603966, 
-83.591175479285, 63.5890000000097, -83.6090000000027, 63.5911765212935, 
-83.6170281586135, 63.5925122124152, -83.6224661396047, 63.5920952941034, 
-83.634601981621, 63.5932055350863, -83.6402616939379, 63.5949999999941, 
-83.6509999999573, 63.5977879418846, -83.6253440389589, 63.6029253017961, 
-83.6194104824602, 63.6052380043218, -83.6185108208848, 63.6039082479539, 
-83.6186369584946, 63.6033361189816, -83.618367011012, 63.6022544982222, 
-83.6174675099837, 63.6035835126533, -83.6149015492998, 63.6025452946933, 
-83.6135559061038, 63.6028186242027, -83.6124732279913, 63.6017905707513, 
-83.6098707106054, 63.59099696475, -83.5610718424074, 63.6442630615399, 
-83.5499769800805, 63.6506818114581, -83.5530239568934, 63.6669884122587, 
-83.5644212506054, 63.662638499707, -83.5725043806037, 63.6602304546174, 
-83.5781904336601, 63.656147042603, -83.581719563286, 63.6551193934227, 
-83.5811196903005, 63.6527622194952, -83.5790278052149, 63.6498004933608, 
-83.5736489091293, 63.6417510328404, -83.5554959793163, 63.6116311512126, 
-83.4868653747897, 63.6024350024344, -83.4707115210052, 63.6029614999885, 
-83.4834692772481, 63.602735018098, -83.4774639912402, 63.6011860724144, 
-83.4647593934505, 63.6010874201247, -83.4631818140136, 63.5982300089556, 
-83.45994518782, 63.5986614355734, -83.4512188842016, 63.6034359494393, 
-83.4256560206912, 63.603728432785, -83.4244099217427, 63.6025724235282, 
-83.423147313588, 63.6008764206355, -83.4210793414048, 63.5957748210365, 
-83.4252094979758, 63.5901654117333, -83.4295599173446, 63.5897569753513, 
-83.434506246785, 63.5887576209523, -83.4432939415976, 63.5897257144902, 
-83.4483492716017, 63.5925883093835, -83.4699609333594, 63.5922884551134, 
-83.4728403562654, 63.5945331895885, -83.4662831348481, 63.6040000000525, 
-83.4540000000214, 63.6461810720551, -83.46960644012, 63.6409031353447, 
-83.4834348695696, 63.6352604734086, -83.4998719416816, 63.6349133522003, 
-83.5009211556846, 63.6255108198363, -83.5210230174712, 63.6214967639128, 
-83.5289757861078, 63.6192129589939, -83.5291044382433, 63.6175837057982, 
-83.529085943243, 63.6170209577546, -83.5288742947174, 63.6137755226763, 
-83.5268115981946, 63.6118310838454, -83.5251122690332, 63.6062709979259, 
-83.514992173046, 63.5916582676385, -83.4866955318266, 63.5898598890744, 
-83.4831191675417, 63.5871559966987, -83.4885591958039, 63.5829608585995, 
-83.4754400643373, 63.580040139598, -83.4765737509994, 63.5800000000199, 
-83.476999999948, 63.5831741015628, -83.4621884306375, 63.5851272272605, 
-83.4527252671606, 63.6012492441811, -83.3923239284265, 63.6040488777313, 
-83.3822057024522, 63.6075704126839, -83.3939893409217, 63.6100348286911, 
-83.4111518446887, 63.618097043813, -83.454669494572, 63.6248527445834, 
-83.570907236233, 63.6220000000212, -83.5789999999807, 63.6286575693412, 
-83.6076033965471, 63.6261433081295, -83.6055571970127, 63.6193041910771, 
-83.5974086552061, 63.6164636509159, -83.595374932895, 63.6136979135253, 
-83.5925818800269, 63.6126579612088, -83.5907412622693, 63.6089765111713, 
-83.5870758702921, 63.6082487390608, -83.5859618160967, 63.5720829924022, 
-83.5312100194144, 63.5719051389767, -83.5332564583787, 63.5689122413223, 
-83.5345580440004, 63.5655729756397, -83.514622985067, 63.5562346827407, 
-83.4921874644453, 63.5529218399003, -83.4857359094345, 63.5524017891449, 
-83.4857568850303, 63.5690090875205, -83.5007195314834, 63.6015304744204, 
-83.5351840194096, 63.622608044794, -83.5631416427293, 63.6284360450707, 
-83.5719548521809, 63.6451335159353, -83.5865753976301, 63.6526491217073, 
-83.5955562006286, 63.6429332494333, -83.6057494341239, 63.6405445621633, 
-83.6080949722699, 63.6370000000047, -83.6119999999859, 63.6315035135559, 
-83.5961341041048, 63.6322627753734, -83.5931156097191, 63.6327280247807, 
-83.5917656400009, 63.6419785972918, -83.5876547138246, 63.6428386007959, 
-83.5871628580786, 63.6427936924745, -83.5846763402643, 63.6420768600949, 
-83.5834677474207, 63.6254796685251, -83.5529065547775, 63.6161298504348, 
-83.540002414245, 63.6083759793122, -83.5256022849415, 63.6041880150095, 
-83.5026411101846, 63.6039372711299, -83.4959734340589, 63.6036596575476, 
-83.4929280282715, 63.6033304049357, -83.4858700475308, 63.602760050569, 
-83.4847376410682, 63.5974879081738, -83.4753449681731, 63.5938842714216, 
-83.4691665482656, 63.5931324782514, -83.4640769498993, 63.6261308804915, 
-83.4451913558373, 63.6340117794964, -83.4421641148717, 63.6375147813199, 
-83.4409551099297, 63.6465985501687, -83.4385207880718, 63.6503411647361, 
-83.5089694459752, 63.6498140401014, -83.5145716803117, 63.6495692760081, 
-83.5163977822104, 63.6460000000174, -83.5369999999339, 63.6470081351189, 
-83.5287500816338, 63.6508762507382, -83.5131938732822, 63.6493211818106, 
-83.5022855712523, 63.6432586237528, -83.4608078560034, 63.6424142675799, 
-83.4564347126704, 63.6420646917217, -83.4457597836738, 63.6402783842529, 
-83.4225003918821, 63.6414351777625, -83.4178756598974, 63.6350000000292, 
-83.4399999999015, 63.6329704383959, -83.4331275073935, 63.6328828465359, 
-83.433261357262, 63.6281595241347, -83.4370222363431, 63.6290917341978, 
-83.4343947604994, 63.6291954940724, -83.4349716783943, 63.6327694204314, 
-83.4416692254409, 63.6326155717918, -83.4421989060863, 63.6326944778311, 
-83.4425639800107, 63.6329999999896, -83.4430000000082, 63.6240000000103, 
-83.4690000000071, 63.6258340276318, -83.4909476336433, 63.6270026216792, 
-83.5137363690733, 63.6278991135052, -83.5369515789602, 63.6279350563775, 
-83.5459295163252, 63.6250000000129, -83.5290000000185, 63.6262333463773, 
-83.5255311284163, 63.6264701223647, -83.5255818821453, 63.631068586656, 
-83.5251777788661, 63.6352334919236, -83.5083299918603, 63.6330000001102, 
-83.5079999999837, 63.6321369345778, -83.500311396951, 63.6325617629284, 
-83.5001862251515, 63.6337006066756, -83.5016452297216, 63.6414261012066, 
-83.5135497090116, 63.6419770863911, -83.5142308355387, 63.6418331239485, 
-83.5149619106238, 63.6321056498945, -83.5020655021592, 63.6320000000667, 
-83.5020000000327, 63.6609228270699, -83.5561328320316, 63.6612673539373, 
-83.5567779801539, 63.6650000000097, -83.5650000000306, 63.671000000487, 
-83.5869999995321, 63.6721550787538, -83.5869145966521, 63.6738596767818, 
-83.5854228619751, 63.6832025165667, -83.5733374567722, 63.6840000000105, 
-83.573999999996, 63.6868934543241, -83.5719838518098, 63.699529566995, 
-83.5492889486395, 63.7073739390839, -83.5085067477294, 63.709522924159, 
-83.5062793928118, 63.7098518392278, -83.5053229483417, 63.7109999999391, 
-83.4979999999974, 63.704950206998, -83.4951174493592, 63.6993545711675, 
-83.4820652922873, 63.6977577152685, -83.4781930603659, 63.686583088042, 
-83.4662442843348, 63.6866282774886, -83.4659467773936, 63.6868520575381, 
-83.462817351718, 63.6883661239732, -83.4479922740349, 63.6877729462605, 
-83.443940760192, 63.6870000000176, -83.43500000002, 63.7068379428437, 
-83.4583091961167, 63.7216587815262, -83.4797499575623, 63.7176522865986, 
-83.4651126667794, 63.7274287104817, -83.4376445643245, 63.7368572082776, 
-83.4126497665829, 63.7336283263886, -83.4174374250826, 63.7207174285436, 
-83.4340985988121, 63.7161203006508, -83.4397693042317, 63.7118711897898, 
-83.4427423248635, 63.7046811156532, -83.4481642195235, 63.7045227435739, 
-83.4483769656129, 63.6932103336267, -83.4850900568138, 63.6929407794755, 
-83.4893184042926, 63.6931042118824, -83.4968676766097, 63.6939585792655, 
-83.5066470428285, 63.6919833450048, -83.5281968276737, 63.6899999999843, 
-83.5360000000087, 63.6822423704179, -83.5514329658092, 63.6811653814537, 
-83.5542264021786, 63.6859999999959, -83.5160000001092, 63.6860000000138, 
-83.5249999998965, 63.6861818396974, -83.5247308328755, 63.6872665613725, 
-83.5197529038739, 63.6876146458438, -83.5197644577564, 63.687473051985, 
-83.5203366199919, 63.6871849728729, -83.5220011652269, 63.6864941589438, 
-83.5239301542501, 63.6713651684532, -83.5674780102749, 63.6680169517905, 
-83.5821350404693, 63.6640133515531, -83.593471300231, 63.6602491976306, 
-83.606299820486, 63.6615456438311, -83.6048441578179, 63.6562086037848, 
-83.6030726066087, 63.6559238335997, -83.5987991612699, 63.654228187929, 
-83.599677486688, 63.6480778676091, -83.5959019886194, 63.6407421067894, 
-83.597327143214, 63.6253083277035, -83.6059507161978, 63.6133212265503, 
-83.5963684307331, 63.5794600354737, -83.5432806421845, 63.5795807561707, 
-83.5434919583362, 63.5856609863796, -83.5546566983918, 63.592453914556, 
-83.561166453312, 63.5945153957953, -83.5629310734407, 63.6020052107801, 
-83.5607195956447, 63.5939380028811, -83.5757085140316, 63.5892893575541, 
-83.5854474110898, 63.5897201549591, -83.6020646438184, 63.5902565504913, 
-83.609362504795, 63.624176776881, -83.6096467215292, 63.6349999999846, 
-83.6169999999945, 63.6512083692661, -83.6273358303221, 63.6493850162863, 
-83.6273860959055, 63.648190180324, -83.625402225518, 63.6393878201672, 
-83.6125517816229, 63.611695744782, -83.5737237755129, 63.606534913914, 
-83.5663637733236, 63.5961260888785, -83.5509945114897, 63.5927658398681, 
-83.5270655985685, 63.5902175267128, -83.52341222817, 63.5906287909519, 
-83.5235292747301, 63.5972270059225, -83.5267597610033, 63.6160433170895, 
-83.5480537168629, 63.6180940392452, -83.5554292768289, 63.6200380676602, 
-83.560922586819, 63.6209999999775, -83.564999999976, 63.6211453121851, 
-83.573583270459, 63.6211753760526, -83.5761482825211, 63.6265655803058, 
-83.5907313588911, 63.6279908511477, -83.5950938213522, 63.6288476325449, 
-83.5972594439676, 63.6288737182292, -83.5983622962938, 63.629000000017, 
-83.612999999991, 63.6339309861382, -83.6234333015672, 63.643831181991, 
-83.6453875285709, 63.636000000016, -83.6210000000186, 63.6372137684553, 
-83.6207437727881, 63.640875235432, -83.6206827558202, 63.642303152822, 
-83.6217564123106, 63.6418022338561, -83.6173374336772, 63.6388030136181, 
-83.6155565660532, 63.6351898829075, -83.6136433023608, 63.6333597270891, 
-83.6130181559741, 63.6305655492865, -83.6105957435395, 63.6266040985919, 
-83.6080105595952, 63.6284836822926, -83.6034946820243, 63.6286753004562, 
-83.60258078807, 63.631885672014, -83.5876154698954, 63.6319307472973, 
-83.5874515258319, 63.6351877583109, -83.5690789950217, 63.6310000000922, 
-83.5670000000483, 63.6262110279829, -83.6162712111872, 63.6228290670453, 
-83.5860647840432, 63.6227067853644, -83.5856683636883, 63.6148383612913, 
-83.5676916306065, 63.6114483049432, -83.5670136544154, 63.61205367665, 
-83.5668518478044, 63.6172761006475, -83.5655526997239, 63.6330664415714, 
-83.5731755867204, 63.6407127116621, -83.5775227992732, 63.6529061399733, 
-83.5864060990062, 63.6777603204973, -83.5908696081089, 63.6784516730713, 
-83.5854507114599, 63.6847243220682, -83.5828055744932, 63.6859999999784, 
-83.582999999993, 63.6851861333703, -83.5823406899819, 63.679606220579, 
-83.5767880442078, 63.6538436017646, -83.5500455496286, 63.6489883391961, 
-83.5449512865486, 63.6486924470686, -83.5443612594867, 63.6482613309587, 
-83.5432871428739, 63.6470000000075, -83.5400000000211, 63.6463014475334, 
-83.5415635365652, 63.6374095784997, -83.5532685982103, 63.6375684796426, 
-83.5562027318512, 63.6410640222309, -83.5484894912786, 63.6413875480952, 
-83.5509508696211, 63.6656379644343, -83.5490148361265, 63.6684674344908, 
-83.548180371565, 63.6632138001349, -83.5366482638884, 63.6605835809768, 
-83.5489782632438, 63.6540000000411, -83.5810000000087, 63.6578440571701, 
-83.6039061008311, 63.6599786602091, -83.616699519579, 63.6745236598144, 
-83.6278913601363, 63.6703911197703, -83.6303331693105, 63.6704840136546, 
-83.6287608953311, 63.6786764740108, -83.6095776879305, 63.6838876043523, 
-83.6003342238657, 63.6985699263875, -83.5832246578684, 63.7325139882119, 
-83.5421275886244, 63.7386244122458, -83.533769946423, 63.7394798949349, 
-83.532442032063, 63.740862404612, -83.5149278807815, 63.7438045517976, 
-83.4580620295699, 63.744162926644, -83.453675189056, 63.7443251645114, 
-83.448119922779, 63.7446864365013, -83.4449526984445, 63.7446557734621, 
-83.4402723538132, 63.7445594528707, -83.4377095851335, 63.74253236468, 
-83.430860224223, 63.7186383467285, -83.4034394805962, 63.7176313158646, 
-83.4025890180365, 63.7119103232548, -83.3997444235449, 63.7109775369203, 
-83.399421230939, 63.7109022371219, -83.3994533913805, 63.7102281866821, 
-83.4002056713833, 63.7109992738017, -83.4062154567746, 63.7121337354425, 
-83.411972276769, 63.718663598489, -83.4429082001164, 63.7326002999759, 
-83.5038711264862, 63.7340216598522, -83.5105148262515, 63.744879662981, 
-83.5207863261191, 63.7400000000213, -83.5519999999534, 63.7551272169206, 
-83.5398797483112, 63.7569637200773, -83.537415865903, 63.757771542451, 
-83.5347012936679, 63.7582808205573, -83.5322816418316, 63.7585435393843, 
-83.5308944951087, 63.7589999995608, -83.5290000000014, 63.7580000004321, 
-83.5289999999965, 63.7463173932647, -83.516005424442, 63.7463209495877, 
-83.5160102670956, 63.745794426284, -83.5180359456587, 63.7455397148211, 
-83.5203122545123, 63.7446981057271, -83.5276272785899, 63.7447165852704, 
-83.5276169140659, 63.7497100941951, -83.5063494951898, 63.750036278705, 
-83.5022548937743, 63.7482436206488, -83.491601307725, 63.7456241330914, 
-83.476050602821, 63.7369816342733, -83.427547167249, 63.7291509213462, 
-83.3940966687168, 63.7286057917113, -83.3922504954325, 63.7247268797458, 
-83.3805642865861, 63.7243794604844, -83.3798503790707, 63.7235236729336, 
-83.3869194960251, 63.7234517162646, -83.3890883757213, 63.7228451484894, 
-83.3950034395162, 63.7129995333838, -83.4690321717991, 63.7092805896754, 
-83.493493773396, 63.7087377611262, -83.4992371166536, 63.6966077488307, 
-83.5254350401604, 63.6958057312103, -83.5272374356895, 63.6878730309654, 
-83.5468450869096, 63.684732153268, -83.5544329624968, 63.6665597747415, 
-83.5920541387222, 63.6580087730763, -83.6051127170358, 63.6544057598106, 
-83.6025466777046, 63.6418248258957, -83.5961179172554, 63.6409091417042, 
-83.5961484642164, 63.6384300780333, -83.5996783015369, 63.6377702031211, 
-83.6007540772418, 63.6163681941052, -83.6363779316655, 63.6108499595868, 
-83.6079282998155, 63.6002532681834, -83.6113928023564, 63.5974676790196, 
-83.6352016195495, 63.5968234512252, -83.6392979460052, 63.6057956118416, 
-83.6112372124297, 63.6134323029429, -83.559749213128, 63.5966183152503, 
-83.5479188956826, 63.5955686233703, -83.5472141413231, 63.5945268365773, 
-83.5707770594382, 63.5949503324384, -83.5735667121993, 63.5950755835356, 
-83.5734953605288, 63.5973405121469, -83.571382783507, 63.6019040253483, 
-83.5627731923458, 63.6053334628684, -83.5691146635181, 63.6097613909752, 
-83.5730315558139, 63.6101673562035, -83.5837552181454, 63.6094512701045, 
-83.6257553074101, 63.6034403215628, -83.7057764079564, 63.6021355809075, 
-83.7140365437081, 63.5949848764086, -83.7141254028055, 63.5918045048293, 
-83.7138275115252, 63.5422865960627, -83.7057841818022, 63.5433321421576, 
-83.701529378208, 63.5442698133778, -83.6892233917657, 63.5423836524437, 
-83.6106842046442, 63.5413512914977, -83.5918897812641, 63.5390737289445, 
-83.580249491149, 63.544191683645, -83.5843964795615, 63.5633980848135, 
-83.6065617734215, 63.578438493782, -83.6144831359607, 63.5928349006309, 
-83.6151502475306, 63.597215817813, -83.6138353969886, 63.6056783711634, 
-83.6111772823961, 63.629218413557, -83.5989763109149, 63.6419682392094, 
-83.5904566993357, 63.6623774530734, -83.5795582336323, 63.6594128026473, 
-83.5720474043066, 63.6573203531152, -83.568151378049, 63.6694627151947, 
-83.6276720922731, 63.6699077265077, -83.6308258246967, 63.6689586112095, 
-83.6247790596308, 63.665472973713, -83.613617402105, 63.6640000000483, 
-83.6130000000295, 63.6642388199208, -83.6154545970654, 63.6647460969484, 
-83.6215358198844, 63.665798725316, -83.6295514191006, 63.6662773267803, 
-83.6288722023687, 63.6699868075841, -83.623884938921, 63.6759998892837, 
-83.6193209191274, 63.6794308948468, -83.6190219123145, 63.6799999999779, 
-83.619000000001, 63.6771596279498, -83.619349336522, 63.6750000000079, 
-83.6219999999405, 63.6764809134895, -83.5939979882971, 63.6737203077784, 
-83.5968891428506, 63.6598014997114, -83.6190581667392, 63.6557955595745, 
-83.6204028875755, 63.6587098292803, -83.6253491550083, 63.6587224687773, 
-83.6253638660229, 63.6587171001983, -83.625552621609, 63.6586804409433, 
-83.6261467399911, 63.6571929017078, -83.6481609923927, 63.6553833208789, 
-83.6491052103427, 63.6552503647638, -83.6507899998285, 63.6518706280151, 
-83.6536251803869, 63.6515960975961, -83.6539460198283, 63.6539486374131, 
-83.6661671469775, 63.6559857543064, -83.6590248377615, 63.6534495637128, 
-83.6592862970841, 63.65164837201, -83.6581038153655, 63.6480422622725, 
-83.6520670332038, 63.6484618147363, -83.5938694207188, 63.6481081776576, 
-83.6137387646152, 63.6488541427973, -83.6623897658351, 63.6440000000474, 
-83.6530000000151, 63.6807896215549, -83.6468784762676, 63.6799701580986, 
-83.645405197694, 63.6642826500892, -83.623163966801, 63.6639999999965, 
-83.623000000101, 63.6630000000107, -83.6319999999134, 63.662693679039, 
-83.6325178428964, 63.6459053755294, -83.6686672453283, 63.6450000000227, 
-83.6699999999848, 63.6472834240414, -83.6671721252637, 63.6476788819236, 
-83.6667042856478, 63.6487322111944, -83.665761950146, 63.652716682376, 
-83.6612413351085, 63.6555758460724, -83.654004991343, 63.6560000771687, 
-83.6520540610052, 63.656462475764, -83.6464334640352, 63.6570793867871, 
-83.6414928852728, 63.6571280434115, -83.6411466830506, 63.6580203925647, 
-83.6335554737155, 63.658000000009, -83.6330000000005, 63.6593821116453, 
-83.6322644899107, 63.6860279476889, -83.6200199631264, 63.6840000000398, 
-83.5980000001465, 63.6896995282465, -83.6391482790585, 63.6870928263719, 
-83.5900468869841, 63.687999999954, -83.593999999944, 63.6861851935466, 
-83.5906321026289, 63.6811537175808, -83.6137009851892, 63.6781750065204, 
-83.6145487987368, 63.6780225853106, -83.6213000852161, 63.6779951641709, 
-83.6236641836159, 63.6775293371328, -83.6424244420256, 63.67600000003, 
-83.6609999999073, 63.679133607306, -83.6499712956107, 63.6799737363794, 
-83.6455462252749, 63.6778048068735, -83.5880940944747, 63.6772872146201, 
-83.5708026808092, 63.6795861240828, -83.5637251965741, 63.6776942170603, 
-83.5627550079071, 63.6770713713256, -83.5618708118907, 63.6786139997936, 
-83.5664718689015, 63.676853412323, -83.5724809793544, 63.6760818587858, 
-83.5742359305138, 63.6726432981973, -83.5821321552441, 63.6626551630711, 
-83.5972281608122, 63.6624331019329, -83.5984126822754, 63.6622481009294, 
-83.5981391674348, 63.6597581328589, -83.5932814783801, 63.6589999999712, 
-83.5919999999826, 63.6392298103815, -83.5656030224769, 63.6368355557863, 
-83.5626811726598, 63.6186826977526, -83.5426193690172, 63.6161414108866, 
-83.5877349954242, 63.6087490670056, -83.6460847511017, 63.5619448432383, 
-83.6455708523175, 63.5556709116897, -83.647330412641, 63.5409149117056, 
-83.6485139604373, 63.5421373984681, -83.6425233269828, 63.5428311444221, 
-83.640032229635, 63.5735052687465, -83.6871869584279, 63.5763429116758, 
-83.6920037583398, 63.6090029631611, -83.6902068312872, 63.6162331353925, 
-83.6896782996359, 63.6169887808385, -83.6898453168069, 63.6371244429278, 
-83.6938881823337, 63.6420000000988, -83.6959999998872, 63.6441804856065, 
-83.7045588987034, 63.6444197485221, -83.6766170458656, 63.6454658240168, 
-83.6692747967367, 63.6530833829585, -83.6537034828235, 63.6531627055543, 
-83.6536142357617, 63.676269199477, -83.6323268659895, 63.6767115189435, 
-83.6320523187995, 63.6828550978921, -83.6444388593945, 63.6851675528125, 
-83.6545716027947, 63.6901457667429, -83.6783518106546, 63.6912958427174, 
-83.6824953831819, 63.7072104608698, -83.6409191310564, 63.7007974906603, 
-83.6248702170924, 63.6996664958254, -83.6218749692867, 63.6999872879098, 
-83.6207283337829, 63.7041827578371, -83.6090227380142, 63.7105157726761, 
-83.5907979268195, 63.7101278356662, -83.590489202345, 63.7051070271538, 
-83.5829308975622, 63.7048650719287, -83.5824989028503, 63.7078556968258, 
-83.5780769586583, 63.705115051457, -83.5624945747637, 63.7004544232356, 
-83.5374810691407, 63.7027971578442, -83.5324874218704, 63.707615140354, 
-83.5332654364638, 63.7075306843041, -83.5347388794292, 63.7071637614308, 
-83.5354425940107, 63.7029656859268, -83.5434949394499, 63.7015148616375, 
-83.546526885538, 63.685252186559, -83.5679198248279, 63.6812407419834, 
-83.5705340350815, 63.6315645390534, -83.578328477974, 63.6318772630023, 
-83.5837406537083, 63.6322617888765, -83.6203456403436, 63.6320753172955, 
-83.6340007802687, 63.6300573866808, -83.6565693370669, 63.6273249061158, 
-83.6775639750989, 63.6253992782196, -83.6889389392531, 63.6042477703017, 
-83.7089978090728, 63.5908803749554, -83.7024677815758, 63.5737373483839, 
-83.6845593165812, 63.5712167598442, -83.6810757315197, 63.5700534557967, 
-83.6796607683207, 63.556367506805, -83.6562797048341, 63.5502172438517, 
-83.6441545105926, 63.5464205693809, -83.6363675724114, 63.5385014321972, 
-83.618103349239, 63.5345865255751, -83.5938057858427, 63.5339997096936, 
-83.587399465215, 63.5256668648726, -83.4913663901307, 63.5249129051654, 
-83.4483409891237, 63.5266541615752, -83.3836403967256, 63.5271202550062, 
-83.3771632164449, 63.5312930582102, -83.3158054486527, 63.5336971312402, 
-83.3036775854143, 63.5365465673985, -83.2938514017709, 63.5534061978643, 
-83.2714078158876, 63.557937246833, -83.267016003283, 63.5641107006042, 
-83.2588213584775, 63.5648493327955, -83.2576040244489, 63.5689738706553, 
-83.2499377483747, 63.5733074638691, -83.2390430618289, 63.5789615250351, 
-83.223617711591, 63.579528938462, -83.2219713391046, 63.59313255453, 
-83.1921992790206, 63.5947698807482, -83.1870176918078, 63.5953035334748, 
-83.1782761017697, 63.5993075896884, -83.1238308885652, 63.5890000000524, 
-83.1250000000376, 63.5871062520997, -83.1297718286236, 63.5838486624578, 
-83.1435205100921, 63.57893325577, -83.1729934105374, 63.5791685883696, 
-83.1733887145274, 63.5793798119947, -83.1746619791606, 63.5737259370049, 
-83.1942210723041, 63.5732372328845, -83.1948966899298, 63.5776477822575, 
-83.2158766170471, 63.5740000000439, -83.2170000000621, 63.5778324189562, 
-83.2432271534724, 63.5770514428628, -83.2468137178889, 63.5770000000056, 
-83.2669999999908, 63.5883633600625, -83.2643557386519, 63.5909999999844, 
-83.2649999999743, 63.5836542867314, -83.1956361990063, 63.5829889963687, 
-83.182953622216, 63.582964141424, -83.1820545090554, 63.5807432107955, 
-83.1710956830054, 63.5833067378982, -83.163901300791, 63.5769056220057, 
-83.1566465365585, 63.5768246992385, -83.1566701145828, 63.5760699113928, 
-83.1603146372268, 63.576297640225, -83.1578493814869, 63.5779380907708, 
-83.13463191853, 63.5776404133965, -83.1334585508086, 63.577211820246, 
-83.1313439975987, 63.5720492899537, -83.11560072197, 63.5714817259869, 
-83.1148995556403, 63.5715326242764, -83.1144295138138, 63.5728870768464, 
-83.1097004748639, 63.5753520002987, -83.104063563437, 63.5757806711009, 
-83.1027899118902, 63.5798884175835, -83.0887343622046, 63.580358428072, 
-83.0873500766502, 63.5826327337909, -83.0807553106963, 63.583593806807, 
-83.0737786880569, 63.5834516202013, -83.072019393229, 63.5837466509788, 
-83.0652441797085, 63.5811247756044, -83.0423873037971, 63.5497151551201, 
-82.9970705616298, 63.5496736104901, -82.9962647507169, 63.5505982658354, 
-82.9882070299581, 63.5509352148036, -82.9861610053995, 63.551474712191, 
-82.9831666634964, 63.5543398682301, -82.9692170258167, 63.5546784323214, 
-82.9674072894264, 63.557908931083, -82.9476226345921, 63.558558943406, 
-82.9405679880727, 63.5601820998017, -82.9335304320674, 63.5612690410979, 
-82.8345240750951, 63.5608432848439, -82.8341784565347, 63.5530355273638, 
-82.8295241722942, 63.5513949411284, -82.8288283011831, 63.5440884948844, 
-82.8261524875425, 63.5440833472746, -82.8261521600042, 63.5440850286116, 
-82.8268007552036, 63.5389786831676, -82.8315430479796, 63.5379360192601, 
-82.8325340347768, 63.5335321042671, -82.8349513640871, 63.5255486686619, 
-82.8429924425405, 63.5255231883932, -82.8430447772952, 63.5022276171246, 
-82.8567044969522, 63.5007083858672, -82.8582283519241, 63.5005359731824, 
-82.8584588434649, 63.4928579094759, -82.8693770660824, 63.4924457273298, 
-82.8698150763685, 63.5005199713875, -82.8686371793722, 63.5045692251329, 
-82.8639463073077, 63.5074943137034, -82.8711594606778, 63.507443128574, 
-82.8665362062926, 63.4961765779341, -82.8110657957374, 63.4933912351989, 
-82.8019590030065, 63.4934745634346, -82.8014716349392, 63.5311486453082, 
-82.7119409028193, 63.6064650370103, -82.6727563751954, 63.6177172284279, 
-82.6732308106963, 63.6299807894842, -82.6769799769328, 63.634401757389, 
-82.6671604403291, 63.6174876232646, -82.6528717434108, 63.624000000847, 
-82.6599999995223, 63.6270823082314, -82.6622256718185, 63.6309740736019, 
-82.6652091041063, 63.6266919690678, -82.7160513746548, 63.6238217330432, 
-82.7219455922197, 63.6251986414917, -82.6782458517516, 63.6340000000511, 
-82.6620000000657, 63.6349999997053, -82.6629999996986, 63.6330000002133, 
-82.6580000002779, 63.6309677509607, -82.7187465798197, 63.6198731075805, 
-82.7331768997231, 63.6170506692716, -82.7398216881817, 63.5981551017397, 
-82.7625349811513, 63.5926002193269, -82.7630077194122, 63.5863482156705, 
-82.753770184923, 63.5772631537048, -82.7390939722994, 63.5715076709437, 
-82.7306539486216, 63.5711340265323, -82.7298625146765, 63.5399581986007, 
-82.6625702611639, 63.5401918242927, -82.6625732665759, 63.5500286438022, 
-82.6610889040993, 63.5508856283743, -82.661021262204, 63.6011009222203, 
-82.6670821390554, 63.6024788836949, -82.6664919722043, 63.5911675009777, 
-82.6597972249086, 63.5910002736337, -82.6591175404943, 63.5973629580048, 
-82.6604972759265, 63.5990319133232, -82.6617179546616, 63.6139765409265, 
-82.6659731253534, 63.6129112003136, -82.6576032381757, 63.6116793245093, 
-82.652611380453, 63.6010000000057, -82.5659999999799, 63.6028848735056, 
-82.546069716561, 63.5724390777752, -82.7118942167591, 63.6196198156982, 
-82.2904577983743, 63.6196966079074, -82.2836005988177, 63.6199388366147, 
-82.2669198694273, 63.6200816238231, -82.2632850212666, 63.623056567024, 
-82.2528502648511, 63.6343170097774, -82.2103349949965, 63.6418876350357, 
-82.1864246924014, 63.6453523294593, -82.1618201902024, 63.6466730788426, 
-82.1371894471663, 63.6471575187222, -82.1513701895639, 63.6482918806952, 
-82.134860804382, 63.6750194626022, -82.1759449658963, 63.683025494817, 
-82.1905215271207, 63.6443510001213, -82.1891821753425, 63.6525254510237, 
-82.1837891808362, 63.6415643129376, -82.1875045121787, 63.591000000008, 
-81.9770000000301, 63.5896911762728, -81.9775150048423, 63.572837789931, 
-81.9672144221441, 63.5691586925461, -81.9643244858457, 63.5647779659875, 
-81.9615155939333, 63.5595950651459, -81.962645586677, 63.5599393492873, 
-81.9616769044638, 63.5600754179938, -81.9600741706373, 63.5591211449525, 
-81.9548857561152, 63.5589848098382, -81.9548404660142, 63.5536169696744, 
-81.9518542810812, 63.5491307340472, -81.9481322162149, 63.5494678554252, 
-81.948155275895, 63.5507775092925, -81.9288454792192, 63.5490093966558, 
-81.9243284245528, 63.5523343739333, -81.9566752349797, 63.5521056626923, 
-81.9560892122139, 63.5462749864996, -81.9442943497264, 63.5547636927455, 
-81.8681907471198, 63.555819290648, -81.8640376563298, 63.5546574902741, 
-81.8586458560515, 63.5149952535767, -81.7055852243841, 63.5147658432785, 
-81.7054544255764, 63.4837547592608, -81.6111507475222, 63.4831952090186, 
-81.6115286899659, 63.4832896024568, -81.6132898975128, 63.4805781975462, 
-81.6131238141397, 63.4553812763899, -81.6127189663155, 63.4504273328808, 
-81.613920676053, 63.4485025258013, -81.6156372864898, 63.4562144470392, 
-81.585455876956, 63.4618626998739, -81.5661766022293, 63.4621443180386, 
-81.565404148846, 63.4621610935866, -81.5643945268588, 63.4630663048257, 
-81.5505852764411, 63.4620178242698, -81.5430331678557, 63.462817853897, 
-81.5154868336642, 63.4582682532326, -81.5255746544127, 63.4587913552982, 
-81.526131676399, 63.4846182003615, -81.5274517449594, 63.4700000000034, 
-81.5759999999896, 63.461768613103, -81.5503520898948, 63.4618927709493, 
-81.5505570082214, 63.4658574548003, -81.5587356473807, 63.4631909131521, 
-81.5556678199062, 63.4689999999913, -81.5659999999848, 63.4639560296703, 
-81.5231851567933, 63.4206616415278, -81.5360613317922, 63.4211941168518, 
-81.5349733705352, 63.418207555473, -81.5312711579412, 63.4067314652261, 
-81.5222742750603, 63.3792151700046, -81.5602345818875, 63.3720427583763, 
-81.5680036048021, 63.3748012666126, -81.3701636752217, 63.3771998824245, 
-81.3633769434973, 63.3837238972798, -81.3647689926052, 63.3872433621479, 
-81.3687426340854, 63.3871138809846, -81.3715081558661, 63.3859069698164, 
-81.3798374966247, 63.3847878022108, -81.3820277141771, 63.3763461276379, 
-81.3965557582275, 63.3665591027946, -81.3024029222555, 63.3548731903413, 
-81.2846561654353, 63.3535412070655, -81.282739574277, 63.3601475899318, 
-81.258571737407, 63.3610540424614, -81.2246235509978, 63.3651089650267, 
-81.1227448171542, 63.3641991989064, -81.1178318080233, 63.3600257661719, 
-81.1015820459242, 63.3612203578628, -81.0894779115953, 63.3607730054837, 
-81.0762999226017, 63.3593911675512, -81.038467065839, 63.3547132558324, 
-81.0299376623369, 63.3596513393909, -81.012482886913, 63.3620524932152, 
-81.0010696388504, 63.365629231583, -80.9874391882563, 63.3622712718297, 
-80.9845370903497, 63.3569882197652, -80.9779640989003, 63.3545629318771, 
-80.9756710093551, 63.3472355141218, -80.928711990856, 63.3464510084596, 
-80.9037713490624, 63.3462375038251, -80.8544434284505, 63.3468321666739, 
-80.8410501484069, 63.3501606558866, -80.8120420831051, 63.3681045939313, 
-80.7608958046206, 63.3702453917555, -80.7571627330517, 63.3904212830315, 
-80.7296271087468, 63.3864125460353, -80.7172566582359, 63.3848280431897, 
-80.7118012782001, 63.3865028573209, -80.6999381702113, 63.3873161473355, 
-80.6960806664415, 63.3873715263269, -80.6941530276126, 63.4129411613672, 
-80.6240542014444, 63.4143170009109, -80.6207932311262, 63.4149142536755, 
-80.6183796985602, 63.4177382526655, -80.6061097974754, 63.4178620939016, 
-80.5981914580231, 63.4183597936384, -80.5894498359984, 63.4203981900376, 
-80.5564756868895, 63.4207969498041, -80.55028903048, 63.4207288532379, 
-80.5335498261966, 63.4200840437985, -80.5258913511118, 63.4200609775534, 
-80.5255762216516, 63.4199120668768, -80.5187920024948, 63.4191482543833, 
-80.4916441335385, 63.4190091434921, -80.4870860247807, 63.4184446622195, 
-80.4728300838725, 63.4183492949449, -80.471034917663, 63.4186917965185, 
-80.460319728778, 63.418556103636, -80.434259913045, 63.4184310140599, 
-80.4290634636822, 63.4181648544145, -80.4118531589129, 63.4197229424391, 
-80.4076832422444, 63.4384565237454, -80.3557938389697, 63.4398514766586, 
-80.3513722662666, 63.4447262665219, -80.3380453031561, 63.5116006227092, 
-80.257537837981, 63.5225873360104, -80.239981549707, 63.5276829500264, 
-80.2317089002819, 63.5272938518923, -80.2305537571092, 63.5224904281773, 
-80.2140271285216, 63.5214576167554, -80.210836685307, 63.5205724424309, 
-80.2081919243032, 63.5116938949017, -80.1844597453446, 63.5098999025064, 
-80.1819748679564, 63.5117610653158, -80.1838806868716, 63.512173065383, 
-80.1835274927441, 63.5124946570618, -80.1828274613492, 63.5116677385696, 
-80.1790857988163, 63.508551909392, -80.1777524854564, 63.5084175851199, 
-80.1780254633135, 63.5053936269061, -80.1751893469466, 63.5045530631225, 
-80.1746384399137, 63.4904099631376, -80.1718543372036, 63.4872583439496, 
-80.1711385558942, 63.4849126778283, -80.170451660517, 63.4751988904916, 
-80.1759285939523, 63.4682031122803, -80.1840311241297, 63.4708107226221, 
-80.1819784258753, 63.4791576321443, -80.1458358544737, 63.4804561295392, 
-80.1418735460079, 63.4818434379324, -80.1392381198873, 63.483136976362, 
-80.1335478143455, 63.4845561510757, -80.1343279836065, 63.4850729341305, 
-80.1344264330746, 63.5086755631008, -80.1182133635251, 63.5125915315003, 
-80.1140928515694, 63.5135191307634, -80.1116763091247, 63.5189999999795, 
-80.0969999999755, 63.4890559157097, -79.9149951250152, 63.4833529857448, 
-79.8853284539323, 63.4875262365117, -79.8869096966806, 63.491794149034, 
-79.8904236651231, 63.4954458146759, -79.8942789546842, 63.5015423432988, 
-79.9029439258875, 63.520801641002, -79.9308950181336, 63.5246812462738, 
-79.9364502639509, 63.5254678661414, -79.9384551345759, 63.529966880908, 
-79.9467463597842, 63.5310477507306, -79.9489085046442, 63.5545076943739, 
-79.9407421118837, 63.5671054089736, -79.936247559896, 63.566903247126, 
-79.9359926831238, 63.5671042730111, -79.9357805579681, 63.5671086748411, 
-79.9363318889489, 63.5692284510064, -79.936758275771, 63.5648621504341, 
-79.9349820136282, 63.5636559398514, -79.9338354872889, 63.5583073174136, 
-79.928758650357, 63.5447377188005, -79.9060585991998, 63.5407519110901, 
-79.8942058140302, 63.5391511052881, -79.8834981600818, 63.5396367931049, 
-79.8763295696224, 63.5422700958777, -79.8633524617019, 63.5243827422425, 
-79.9539662722359, 63.5108626250505, -80.0108595991791, 63.5092400010397, 
-80.0154068134509, 63.5088621703333, -80.0158952597121, 63.5086908155059, 
-80.016238814619, 63.5093171935773, -80.020790799599, 63.5239982253075, 
-80.0392499762406, 63.5276088223369, -80.0421737824498, 63.531707080295, 
-80.0482076481876, 63.5378334358352, -80.0569352914106, 63.5394246383993, 
-80.0590281320119, 63.5363686243828, -80.1015984900082, 63.5336404907974, 
-80.1071113043779, 63.5324462961734, -80.1104264114129, 63.5322122174001, 
-80.1109764427768, 63.5309638395973, -80.1088039635002, 63.5336868969802, 
-80.0873304760072, 63.533766580098, -80.0815818468484, 63.5337249751537, 
-80.0761379859295, 63.5352510060194, -80.0701822943138, 63.5364250606937, 
-80.0677208624791, 63.5415987334865, -80.060385414581, 63.5475927259651, 
-80.0464660226631, 63.5491891558793, -80.0402434788928, 63.5673859373996, 
-79.9970920542624, 63.584989952762, -79.9624006151836, 63.6568116249459, 
-79.8643845390168, 63.6018780921089, -79.8489647225652, 63.5796334505117, 
-79.8348592797452, 63.5796014061348, -79.8351223776225, 63.5745812390254, 
-79.8928224361283, 63.5730759957044, -79.9080220109947, 63.5679157528772, 
-79.9060025642878, 63.5677542617926, -79.9503721417278, 63.5674225128516, 
-79.9559862391461, 63.5433076435319, -79.9576289159816, 63.5439088349188, 
-79.9687717083419, 63.5128391528579, -80.0396915143002, 63.5112699339102, 
-80.0432475854812, 63.5095632559894, -80.0460729679617, 63.5056179246875, 
-80.0526526960781, 63.4991122908406, -80.0615647011047, 63.5089406478149, 
-80.070461812786, 63.5109334546351, -80.0727865656254, 63.5139378179438, 
-80.0735998115787, 63.5156411138794, -80.0831594714128, 63.5107472677211, 
-80.0955494854399, 63.4972175363196, -80.126804121455, 63.4890242946703, 
-80.1443606643249, 63.4859501197986, -80.1509217475358, 63.4780371490917, 
-80.1623516622511, 63.4848736937956, -80.1592818532358, 63.4868159354436, 
-80.1585468365425, 63.4929750332125, -80.1561926667001, 63.4905198588952, 
-80.1579391836638, 63.4825346738407, -80.1631827555856, 63.4805092341406, 
-80.1638469414217, 63.480481670331, -80.1638358190413, 63.4754795282074, 
-80.1658077976672, 63.4659413298152, -80.1671386028076, 63.4605516828541, 
-80.1684521544387, 63.4650918576882, -80.2187299848543, 63.4684020604978, 
-80.2224010454207, 63.4827582804913, -80.2376885504572, 63.4808394638133, 
-80.2366022575549, 63.4775481661223, -80.234130587633, 63.4739999999745, 
-80.2310000000268, 63.4684325606035, -80.2370703472809, 63.4616078037417, 
-80.2519875664501, 63.4609723136055, -80.2533179382652, 63.4140092319398, 
-80.3498635150735, 63.4169870881895, -80.2690892545457, 63.4134272105844, 
-80.1629817336247, 63.4124818991836, -80.1537076092863, 63.4535369034729, 
-80.1935666518198, 63.4431675038188, -80.1977070517035, 63.4312682971461, 
-80.203347140508, 63.4251411242442, -80.2083537780712, 63.4244069763398, 
-80.2088475144128, 63.3999282546477, -80.2265931562244, 63.3840000000353, 
-80.2240000000031, 63.3829211817465, -80.2239446979413, 63.3822201090303, 
-80.2242854592759, 63.3823853969394, -80.2220587148931, 63.382150160659, 
-80.2188948102959, 63.3826299270987, -80.218032539312, 63.384187890642, 
-80.2254089461073, 63.3905347236804, -80.2550737542035, 63.394111396948, 
-80.2562574512393, 63.395047113279, -80.2590003199226, 63.3972919833168, 
-80.2437725028402, 63.4019999999209, -80.2150000000131, 63.3852307355369, 
-80.2036725371956, 63.3744582905377, -80.1985645262984, 63.3856649476308, 
-80.2361812610157, 63.3867712431805, -80.2458572135162, 63.3871060133347, 
-80.2479554184777, 63.3848322092745, -80.2400368360232, 63.3786816493752, 
-80.2237540057053, 63.3413994758546, -80.1976062049978, 63.3314340651176, 
-80.1869148820795, 63.3252788344552, -80.1830907982854, 63.3232818231807, 
-80.1819955097258, 63.2892429316121, -80.1647151133107, 63.286952042805, 
-80.1637649265125, 63.2666279609809, -80.1423297421823, 63.278738128782, 
-80.1530752957464, 63.2984126437618, -80.1737739719092, 63.3156697113128, 
-80.1891671343986, 63.3208973371665, -80.1937752339001, 63.3310958866325, 
-80.2022264056582, 63.3507667843639, -80.2139148651664, 63.3511808403607, 
-80.2150585343676, 63.3507338883448, -80.2423774413185, 63.3393795080167, 
-80.2698698024176, 63.3802122149761, -80.1754316834271, 63.3460454884597, 
-80.1075663275331, 63.3454923230203, -80.106419152391, 63.3410476505847, 
-80.0954055639145, 63.3319140187447, -80.0766120096927, 63.3123015340565, 
-80.0524812953503, 63.3058380527939, -80.0454748102486, 63.2707697110487, 
-80.0169853479767, 63.2568371795758, -80.003015549474, 63.2629414577197, 
-80.0027514360801, 63.3022176581869, -80.0079714260556, 63.3301258808617, 
-80.0362308039317, 63.3524154488326, -80.0620643753121, 63.3720052460458, 
-80.0792654449674, 63.3720096660234, -80.0814442351688, 63.3720057429454, 
-80.0981751398462, 63.3687585315838, -80.1040486927216, 63.3682639018947, 
-80.1058274453765, 63.3654472512744, -80.1140142739209, 63.364808879942, 
-80.1144786676749, 63.365046346351, -80.1247410004876, 63.3666484574391, 
-80.1284066223199, 63.3666941493117, -80.1284665589048, 63.3728573004584, 
-80.1289716324615, 63.378583561014, -80.1284248603953, 63.3828041896743, 
-80.1297438666702, 63.3838112465743, -80.130850300205, 63.391485228998, 
-80.1401867243855, 63.4239114327397, -80.1865375694158, 63.4127867927161, 
-80.1972574801185, 63.4081745584037, -80.2016797333116, 63.3823538675995, 
-80.2161499665811, 63.3585881669799, -80.2266510135541, 63.356417326153, 
-80.22836093179, 63.3584242151441, -80.2404324410128, 63.3434261247515, 
-80.2294796763426, 63.341309048079, -80.2286141390992, 63.3146086074236, 
-80.2236798040179, 63.3145006289303, -80.2237122609489, 63.3072451199372, 
-80.2242176813027, 63.2898757274538, -80.2269317866083, 63.2768578374596, 
-80.2318452643225, 63.2699646292103, -80.2384796064938, 63.2680108034944, 
-80.217262102106, 63.265876836675, -80.2086952483014, 63.2586921115689, 
-80.167744052479, 63.2718464286586, -80.1662391594215, 63.2787087759891, 
-80.1648575053204, 63.2807152309712, -80.1642924202843, 63.2875759560972, 
-80.159745408175, 63.2891341103373, -80.1565212618636, 63.2927942511491, 
-80.1486752883388, 63.2953047647647, -80.1320688312902, 63.2963187803444, 
-80.1275293976802, 63.3074778521706, -80.1270449560306, 63.3149943691116, 
-80.1263223458923, 63.3183202780009, -80.1261946857577, 63.3215161590757, 
-80.1260699372798, 63.3232407732434, -80.1240212201479, 63.3270964703731, 
-80.1194747382092, 63.3322545326936, -80.1146752467709, 63.3350723182584, 
-80.1117057708549, 63.3372016786087, -80.1106197581208, 63.3391599775189, 
-80.1101402999826, 63.353969198358, -80.0966447068776, 63.3572725154634, 
-80.089056641392, 63.3608694585346, -80.0861760949176, 63.365920863995, 
-80.0673812873663, 63.3677684855422, -80.0609232972724, 63.3731365253157, 
-80.0421082067161, 63.3800759330391, -80.0162316872152, 63.3673495633954, 
-79.9854465397434, 63.3715407924771, -79.9482698107084, 63.3748495376061, 
-79.9206720369834, 63.3749627582351, -79.9191840850407, 63.3730804356316, 
-79.9099182812083, 63.366531612375, -79.893622027418, 63.3611434897761, 
-79.8860465643874, 63.3541152782376, -79.8773140891183, 63.3496318856381, 
-79.867085280858, 63.3475381358498, -79.8614102215178, 63.3396404487444, 
-79.8441496792732, 63.3127396427887, -79.8012072434106, 63.310744281555, 
-79.7982948026577, 63.248454687474, -79.7366215606674, 63.27642697006, 
-79.7516255662381, 63.352195345984, -79.8027700859813, 63.3693366183266, 
-79.8140563469665, 63.3866243669923, -79.8315390076752, 63.3907929109471, 
-79.8345603926312, 63.3971802154792, -79.8333523304265, 63.3985143097045, 
-79.8301141475724, 63.3997175438762, -79.8298521779291, 63.3988116870935, 
-79.838576627673, 63.3971423066145, -79.8525344088181, 63.3983052618189, 
-79.8543937444914, 63.4003432699697, -79.8563120871355, 63.3992934638375, 
-79.8608610291424, 63.3836084092319, -79.9304269247031, 63.3785735155812, 
-79.9472713344426, 63.3944639527629, -79.9252995599491, 63.4038321970598, 
-79.9139630163351, 63.4077560277177, -79.9096054349533, 63.4179686485448, 
-79.8963849471534, 63.4191736501042, -79.890128661893, 63.4233047075409, 
-79.8483762639272, 63.4323442339068, -79.9051534747298, 63.4301701671102, 
-79.9129622952749, 63.4330081678731, -79.9184843280628, 63.4347040858014, 
-79.9364437831337, 63.4348108604264, -79.9467200277584, 63.439797550741, 
-79.9635894991195, 63.4442399011768, -79.9805571236913, 63.4459014509361, 
-79.98594034145, 63.4484192819605, -79.9936676016105, 63.4754038866443, 
-80.0004219358615, 63.4774428684042, -80.0011599172889, 63.493521323869, 
-80.0137630145455, 63.4944234949806, -80.0230674354213, 63.4952606011054, 
-80.029031108597, 63.5029195938108, -80.0444603413099, 63.50401720318, 
-80.0469773497554, 63.5071473865971, -80.060123447555, 63.5139975864888, 
-80.0853119934546, 63.5152742559155, -80.1144796878266, 63.5113556225207, 
-80.1459068616791, 63.5110647839961, -80.1515934443421, 63.5209751941391, 
-80.1717677016239, 63.495842692215, -80.1114929314552, 63.5061389095895, 
-80.0770263427855, 63.5113633282031, -80.0568779687229, 63.5125978113061, 
-80.0518856777295, 63.5370648578809, -80.0112254213992, 63.5345109233585, 
-80.0102140485749, 63.5297031972332, -80.0070002292541, 63.5112681925925, 
-79.9951943542467, 63.5064745587969, -79.992025229878, 63.5041015544722, 
-79.9900474031063, 63.5065252129096, -79.9780604488059, 63.5067326639428, 
-79.9733452213823, 63.5070470321731, -79.9219217938579, 63.5064365701797, 
-79.9034978819517, 63.5073904653802, -79.8933259050669, 63.5129058846131, 
-79.9325314335279, 63.5128153223801, -79.9414054459586, 63.5111639934147, 
-79.9758763723973, 63.510959524051, -79.980283611421, 63.5056890444918, 
-80.0501977925867, 63.5025318322668, -80.0596175221568, 63.5001727980949, 
-80.0638209862949, 63.5022472455593, -80.0680892078885, 63.5052618731335, 
-80.0767793604295, 63.5070607450317, -80.0819807465851, 63.5084938100106, 
-80.0947792456426, 63.5248103331934, -80.086788147066, 63.5336209677646, 
-80.0849059068913, 63.5374284349485, -80.0826939495818, 63.5393018764323, 
-80.0767803918833, 63.5452349589605, -80.0504142575505, 63.5463617500641, 
-80.0449553371211, 63.5472992550647, -80.0400805061808, 63.5666866727957, 
-80.0527219407505, 63.5681058134578, -80.0534275299652, 63.5588118261249, 
-80.0584592495155, 63.5576552101364, -80.059033061802, 63.5542551599783, 
-80.0595249323302, 63.5470874067358, -80.0639159342977, 63.5459531534652, 
-80.0639915684069, 63.5456166474295, -80.0769366095724, 63.5455408374703, 
-80.0794210632008, 63.543929469905, -80.0731645989188, 63.5372249345265, 
-80.0586875670323, 63.5384485100349, -80.0583893971679, 63.5403844892577, 
-80.0574782433487, 63.5443657131524, -80.0581000543932, 63.5472103618312, 
-80.0563054775382, 63.5479979808993, -80.0553004942441, 63.5563032900907, 
-80.0492638906017, 63.5563342448935, -80.0484850049798, 63.5651421261091, 
-80.0510987330628, 63.5679960613467, -80.0527455069288, 63.5754882656288, 
-80.0555339516856, 63.5841498244381, -80.0596662248374, 63.5863687630649, 
-80.0608379109949, 63.5871095196337, -80.0681422212838, 63.5870468680886, 
-80.0696283115135, 63.5896052468147, -80.0708666106726, 63.5901578186774, 
-80.0707539896523, 63.5930801112606, -80.0706893334101, 63.5927137821768, 
-80.0714006458548, 63.589822836708, -80.0820471873737, 63.5892902761466, 
-80.0830380460711, 63.5883288981913, -80.0844046245738, 63.5876636251103, 
-80.0915174791015, 63.5895746968948, -80.099707353576, 63.5900338340295, 
-80.1019910903719, 63.5984842109685, -80.1242343953823, 63.5989817293361, 
-80.1274439477202, 63.6038841382537, -80.1269251797076, 63.6074473195316, 
-80.1263713940544, 63.6091971117552, -80.1258787884094, 63.6095066887591, 
-80.1147364703238, 63.6099505163533, -80.0914827789626, 63.6120010760077, 
-80.095387964433, 63.6113129601808, -80.0975442493586, 63.6117723364138, 
-80.0954380740319, 63.6122567533527, -80.0923986995617, 63.6139251338219, 
-80.0839944452861, 63.6143536309347, -80.0799311690604, 63.6139966052848, 
-80.0780832852316, 63.6139863741402, -80.0766110650742, 63.6060202255576, 
-80.0618478911559, 63.6000460738272, -80.0349624630663, 63.5990906836908, 
-80.0318143719674, 63.5981673460284, -80.028259916016, 63.6008035792409, 
-79.9992862229816, 63.6012310171303, -79.9924605328018, 63.6014096616702, 
-79.9874647460672, 63.6040242016595, -79.9523110490587, 63.6070657248004, 
-79.9045221562087, 63.603244226206, -79.8954295223628, 63.5918339990879, 
-79.8695968196847, 63.5892336842287, -79.8641863990466, 63.5884421959444, 
-79.8632814842415, 63.5807079536989, -79.8545358130681, 63.586394691073, 
-79.8522422534008, 63.5891658715009, -79.8514569036918, 63.6132614325028, 
-79.8478689831964, 63.6243122751819, -79.838735286861, 63.626724105094, 
-79.8362124102101, 63.6311560969401, -79.8401262041155, 63.6319855778281, 
-79.8327296039411, 63.6519028120488, -79.7943978590216, 63.6520778260299, 
-79.8002917208811, 63.6522855193405, -79.7991111553767, 63.6534248104324, 
-79.7988700678135, 63.6634759847642, -79.7881262708772, 63.6647110379601, 
-79.7845900755339, 63.6618910069769, -79.7334025703777, 63.6620180242812, 
-79.7155666007072, 63.6614609602819, -79.7138793065747, 63.6491320789934, 
-79.6830049518848, 63.6634952215822, -79.6738380649573, 63.6834869530504, 
-79.6731164029416, 63.6958657085672, -79.6350309475544, 63.6901495673955, 
-79.611561847792, 63.689999098907, -79.6108306998922, 63.6696812663111, 
-79.5771550993157, 63.6700325465629, -79.5786267848492, 63.6720587338905, 
-79.593614935581, 63.6720250585858, -79.5958678554114, 63.6656407930496, 
-79.6146355306319, 63.6679406927817, -79.6151011327508, 63.6701032814469, 
-79.6157451344265, 63.6800936831081, -79.6431792686609, 63.6888723750525, 
-79.6943027395103, 63.6925935024229, -79.7062913872916, 63.6993055080552, 
-79.7368221210645, 63.7004681270954, -79.7368490858562, 63.7080951828927, 
-79.7286141575244, 63.709082103831, -79.727794333038, 63.7102696748326, 
-79.7249442787769, 63.705503186144, -79.7224875358778, 63.7075004079756, 
-79.7059814648926, 63.7098414343736, -79.7034095686348, 63.7075321652461, 
-79.6744640077563, 63.7323776739957, -79.6782986101025, 63.7389999999242, 
-79.6760000000167, 63.7275516422003, -79.6814571522944, 63.7047975217887, 
-79.6817667097325, 63.7017709767245, -79.6817553231507, 63.6964435676995, 
-79.6817860760667, 63.6788021721199, -79.6810834301646, 63.6764589047193, 
-79.6811040469195, 63.6602793997611, -79.6785503547393, 63.6591041475817, 
-79.6784395754069, 63.661400732334, -79.6800418808558, 63.674477980123, 
-79.689586078094, 63.6787478142651, -79.6946601702587, 63.6790798063463, 
-79.6957455622445, 63.6795087798156, -79.6968722155238, 63.680992697377, 
-79.7021153260438, 63.6813523268886, -79.6992109024985, 63.6817439482546, 
-79.6940326256915, 63.6814211977931, -79.6868097532506, 63.6787815528624, 
-79.6672247872075, 63.6791524975065, -79.6679797005175, 63.6801223875958, 
-79.6698480540311, 63.6808975828356, -79.6675878593475, 63.6843745743433, 
-79.6569985355907, 63.6851027934315, -79.6433542933937, 63.6850532556625, 
-79.6436485252834, 63.6857313683542, -79.6431161933348, 63.6876039620096, 
-79.6416417046901, 63.6868834925804, -79.6403517439633, 63.6826443719711, 
-79.6351240406619, 63.6734167812735, -79.6256095244404, 63.6701754637432, 
-79.6241574779762, 63.6693544940509, -79.6234128568976, 63.6748819677843, 
-79.5952265790002, 63.6751764331067, -79.5934088690818, 63.6745217429906, 
-79.5936017399783, 63.6718158474668, -79.5941199139835, 63.6632331876766, 
-79.5897117659782, 63.662529343918, -79.5862997451234, 63.6620766622081, 
-79.5560320381349, 63.6617610894107, -79.5552960441259, 63.665707078471, 
-79.5804442049573, 63.6584093389665, -79.6106743355275, 63.662552555122, 
-79.6134056158576, 63.6649178821297, -79.6147613616155, 63.6657804094853, 
-79.6153951824513, 63.6741106236564, -79.6180847557732, 63.6798073645371, 
-79.6091306118224, 63.6797194405435, -79.6092692735991, 63.6772632823762, 
-79.6098586674495, 63.6761911333839, -79.6119283692145, 63.6526435058808, 
-79.6614158079009, 63.637066916086, -79.6799292541213, 63.650702393195, 
-79.686308580452, 63.6541539043326, -79.6885424349917, 63.6571159367565, 
-79.6905461775705, 63.6583922003069, -79.6880224204445, 63.6610691898735, 
-79.6852494964526, 63.6606955723941, -79.678620318335, 63.6608323503689, 
-79.6750925053714, 63.6571781446355, -79.6724779911804, 63.6334448886236, 
-79.654085153287, 63.6318267174387, -79.65290645814, 63.6222940383448, 
-79.6468779900872, 63.6039999999347, -79.6120000000117, 63.6083775602782, 
-79.6110266774595, 63.6532242633022, -79.6373392027474, 63.6519476430991, 
-79.7002951310072, 63.6509399826267, -79.7050893308744, 63.6421936628227, 
-79.7131622722129, 63.6418161978088, -79.7170835824397, 63.6398128681762, 
-79.730803158093, 63.6369710387806, -79.741393886957, 63.6368392601382, 
-79.741595630794, 63.637423311382, -79.7402785468112), .Dim = c(2L, 
3417L))

```



```{r}

fitTrack(anim, silent=TRUE)

```

After estimating, the `Animal` object has been updated with the results.

```{r}

anim

```

This is also evident when plotting the object.

```{r, fig.cap = "Default plot of a fitted animal class."}

plot(anim)

```

Not only the `Animal` class, but also the `Measurement` and `Movement` class are updated.

```{r}

mov

```

Because the random walk model does not have any movement parameters, this can not be seen when printing, but if we plot the object, the estimated locations are changed.

```{r, fig.cap = "Default plot of a fitted movement class."}

plot(mov,sd=FALSE)

```

The estimated track and its standard errors can be extracted with the function `getTrack`.

```{r}

head(getTrack(anim))

```



# Simulating data


To simulate from the state-space model (or any part of it), the `simTrack` function can be used. The following code simulates observations. The first argument is a `Measurement` class, specifying the model to simulate from; the second argument is the number of replications, while the third argument is an `Observation` class, which specifies the time points and location classes to use. The parameters used is the result from `fitTrack`. If `fitTrack` has not yet been used on the object, the initial parameters are used.

```{r, fig.cap = "Plot of simulated observations"}

set.seed(123)
sobs <- simTrack(meas,1,obs)
plot(t(sobs[,,1]), pch = 16, col= rgb(0,0,0,0.3), xlab = "x", ylab = "y")

```

By plotting the simulated observations seperately for each location class, we clearly see how the variance increases with the location class.

```{r, fig.cap = "Plot of simulated observations per location class", results='hide'}

layout(matrix(1:6,3))
sapply(2:7,function(i)
    plot(t(sobs[,as.numeric(obs$qual)==i,1]),
         pch = 16,
         xlab = "x", ylab = "y", main = levels(obs$qual)[i],
         col= rgb(0,0,0,0.3),
         ylim = range(sobs[2,,1]),
         xlim = range(sobs[1,,1]))
    )

```

Likewise, the function can be used on a `Movement` class. The first argument is the 'Movement' class to simulate from, the second argument is the number of replications, and the third argument is the initial position. If an initial position is not given, (0,0) is used.

```{r, fig.cap = "Plot of simulated movement"}

set.seed(456)
smov <- simTrack(mov,1, c(0,0))
plot(t(smov[,,1]), xlab = "x", ylab = "y")

```

If the `simTrack` function is used on an `Animal` object, both movement and observations are simulated according to the full state-space model. Further, a new `Animal` object is returned. Note, that only the observations are changed from the object used in the simulation.

```{r}

set.seed(789)
sa <- simTrack(anim,1)
## Save the new Animal object as an2
an2 <- sa[3,1]$Animal
an2
plot(an2)

```

The new `Animal` object can be used directly in `fitTrack` to update the parameter values and estimated locations.

```{r,warnings=FALSE}

fitTrack(an2, silent = TRUE)

```

Now, the new object is updated

```{r, fig.cap = "Plot of estimated locations for the simulation"}

an2

plot(an2)

```

The estimated parameters can easily be compared to the parameters used in the simulation. Below are the true and estimated variance parameters for the movement model.

```{r}

anim$movement$varianceParameters
an2$movement$varianceParameters
## vcov is the covariance of both movement and variance parameters
2 * sqrt(diag(an2$movement$vcov))

```


# References
